### 2016-02-27 ml_notes/draft.tex
- initial commit with files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% ICML 2016 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[icml2016,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}

% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}

% For citations
\usepackage{natbib}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2016} with
% \usepackage[nohyperref]{icml2016} above.
\usepackage{hyperref}

% Packages hyperref and algorithmic misbehave sometimes.  We can fix
% this with the following command.
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
\usepackage{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
%\usepackage[accepted]{icml2016}

%-------------------------------------------------------------
%                      Own Commands
%-------------------------------------------------------------
\usepackage{amsmath}
\newcommand{\cbn}{\textsc{Cbn}}
\newcommand{\bn}{\textsc{Bn}}

\renewcommand{\algorithmiccomment}[1]{/* #1 */}
\def\ci{\perp\!\!\!\perp}
\def\dep{\perp\!\!\!\perp\!\!\!\!\!\!\!/\,\,\,\,}
% Theorem & Co environments and counters
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{equat}[theorem]{Equation}
\newtheorem{example}[theorem]{Example}
%-------------------------------------------------------------
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\etal}{\emph{et al.}}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\cf}{\emph{cf.}}
\newcommand{\diff}[2]{\frac{\partial #1}{\partial #2}}
%\newcommand{\diff}[2]{\nabla_{#2}{#1}}
\newcommand{\vct}[1]{\ensuremath{\boldsymbol{#1}}} %for greek letters
\newcommand{\mat}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\set}[1]{\ensuremath{\mathcal{#1}}}
\newcommand{\con}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\T}{\ensuremath{\top}}
\newcommand{\mycomment}[1]{\textcolor{red}{#1}}
\newcommand{\ind}[1]{\ensuremath{\mathbbm 1_{#1}}}
\newcommand{\argmax}{\operatornamewithlimits{\arg\,\max}}
\newcommand{\erf}{\text{erf}}
\newcommand{\argmin}{\operatornamewithlimits{\arg\,\min}}
\newcommand{\bmat}[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand{\mname}{\texttt{OLCS}}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Machine learning working notes}

\begin{document}

\twocolumn[
\icmltitle{Machine Learning Working Notes}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2016
% package.
\icmlauthor{Huang Xiao}{xiaohu@in.tum.de}
\icmladdress{Technische Universit\"{a}t M\"{u}nchen,
	Boltzmannstr.3, D-85743 Garching b. M\"{u}nchen, Germany} 
%\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
%\icmladdress{Their Fantastic Institute,
%            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine learning}

\vskip 0.3in
]

\begin{abstract} 
	Machine learning is a fast pacing discipline in many working fields, especially it is now regarded as the most impacting subject in artificial intelligence. In this working notes, I summarize some important notes during my study of machine learning. For the completeness, references are included for readers who are reading this article. Note that this working note is only distributed and shared with author's acknowledge and confirmation. It is not intended as a publishable research paper or tutorial.

\end{abstract}

\section{Gaussian Process Regression}
\label{sec:gpr}
Gaussian process is an important nonparametric regression model which looks for an optimal functional in a space of functions, that minimizes a loss function, although the loss function needs not to be explicitly defined. \cite{rw06gp}

Give a training dataset $\set D = \left\{x_i\right\}_{i=1}^n$ with $x_i \in R^d$, \textit{i.i.d} drawn from certain distribution, we are interested at the predictive distribution of unknown target for the  test sample $x_*$, denoted as $f_*$. Suppose a prior over $\vct y$ given input $\vct X$ is a $n$-variable Gaussian distribution, 
\[
\vct y \sim \set N(\vct 0, K(\vct X, \vct X)) 
\]
where $K(\vct X, \vct X)$ defines a covariance function over $\vct X$. Therefore the posterior of $f_*$ given the training dataset $\set D$ is also a Gaussian. 
\[
f_*|\vct y, \vct X, x_* \sim \set N(\mu_*, \Sigma_*^{-1})
\]
where the sufficient statistics can be derived using Bayesian theorem, 
\begin{align}
	& \mu_* = K_{X_*,X}\left[K_{X,X}+\sigma_n^2 I\right]^{-1}\vct y \label{eq:gpr_mu}\\
	& \Sigma_*^{-1} = K_{X_*,X_*} - K_{X_*,X}\left[K_{X,X}+\sigma_n^2 I\right]^{-1}K_{X,X_*} \label{eq:gpr_cov}
\end{align}
where $\sigma_n^2$ is the noise level and $K_{\cdot,\cdot}$ represents a shorthand for covariance matrix.

To obtain the Eq.\eqref{eq:gpr_mu}-\eqref{eq:gpr_cov}, we can use the following trick. 
Given two variables $(\vct x, \vct y)$ following a Gaussian distribution,
\[
\bmat{\vct x\\ \vct y} \sim \set N\left( 
\bmat{\mu_x \\ \mu_y}, \bmat{A & C \\ C^T & B}
\right)
\]
Then we have the conditional distribution,
\[
\vct x|\vct y \sim \set N\left(\mu_x+CB^{-1}(\vct y - \mu_y), A - C^TB^{-1}C \right)
\]
\bibliography{myrefs}
\bibliographystyle{icml2016}

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was
% created by Lise Getoor and Tobias Scheffer, it was slightly modified  
% from the 2010 version by Thorsten Joachims & Johannes Fuernkranz, 
% slightly modified from the 2009 version by Kiri Wagstaff and 
% Sam Roweis's 2008 version, which is slightly modified from 
% Prasad Tadepalli's 2007 version which is a lightly 
% changed version of the previous year's version by Andrew Moore, 
% which was in turn edited from those of Kristian Kersting and 
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2016-02-27 basics/src/QuickSort.scala

@@ -1,0 +1,10 @@
+/**
+  * Created by morgan on 27/02/16.
+  */
+object QuickSort {
+
+    def main(args: Array[String]) {
+        println("Hello Scala!")
+    }
+
+}

### 2016-03-17 basics/src/QuickSort.scala
add scripts folder

@@ -4,7 +4,10 @@
 object QuickSort {
 
     def main(args: Array[String]) {
-        println("Hello Scala!")
+
+        val s = "hello.."
+        println("string length is " + s.length())
+
     }
 
 }

### 2016-03-17 scripts/get_icml_statistics.py

@@ -1,0 +1,65 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+import json
+import urllib
+import sqlite3
+
+# open DB
+try:
+    dbconn = sqlite3.connect('../h3db/AIAcademicBase.sqlite3')
+    dbcur = dbconn.cursor()
+except sqlite3.Error as e:
+    print "[h3err] An error is occured: ", e.args[0]
+
+# create table icml_authors if not exists
+dbcur.execute('''
+    CREATE TABLE IF NOT EXISTS icml_authors(
+        name TEXT NOT NULL,
+        affiliation TEXT DEFAULT 'N/A',
+        country TEXT DEFAULT 'N/A',
+        email TEXT,
+        n_appeared INTEGER DEFAULT 1) ''')
+dbcur.execute(''' CREATE INDEX IF NOT EXISTS idx_author on icml_authors(name) ''')
+
+# source_icml: kimono crawled data hosted on firebase
+results_icml11 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/9dddmfj6/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+results_icml12 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/4zpjozlw/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+results_icml13 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/bpcqdplm/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+results_icml14 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/3bvqawso/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+results_icml15 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/3al38z4q/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+
+# icml_exist_authors = dbcur.execute('select name from icml_authors').fetchall()
+
+# save new authors found in data source
+for row in results_icml11[u'results'][u'collection1']:
[…]

### 2016-03-17 scripts/get_nips_statistics.py

@@ -1,0 +1,69 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+import json
+import urllib
+import sqlite3
+import re
+
+# open DB
+try:
+    dbconn = sqlite3.connect('../h3db/AIAcademicBase.sqlite3')
+    dbcur = dbconn.cursor()
+except sqlite3.Error as e:
+    print "[h3err] An error is occured: ", e.args[0]
+
+# create table icml_authors if not exists
+dbcur.execute('''
+    CREATE TABLE IF NOT EXISTS nips_authors(
+        name TEXT NOT NULL,
+        affiliation TEXT DEFAULT 'N/A',
+        country TEXT DEFAULT 'N/A',
+        email TEXT,
+        n_appeared INTEGER DEFAULT 1,
+        avc_position REAL) ''')
+dbcur.execute(''' CREATE INDEX IF NOT EXISTS idx_author on nips_authors(name) ''')
+
+# source_icml: kimono crawled data hosted on firebase
+results_nips11 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/7dcecg3s/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+results_nips12 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/5qyt8h4c/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+results_nips13 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/dif28pwm/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+results_nips14 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/bk7nfs6a/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+results_nips15 = json.load(urllib.urlopen(
+    "https://crawlydb.firebaseio.com//kimono/api/24mdcuum/latest.json?auth=GcbFpZq0UqoadmWMQiKGY0nydNTCjlL25c5dSpL7"))
+
+# save new authors found in data source
+pattern = re.compile(r"\s[A-Z]{1}[.]\s")
+for row in results_nips15[u'results'][u'collection1']:
[…]

### 2016-03-17 scripts/process_nips_authors_names.py

@@ -1,0 +1,14 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+import sqlite3
+
+dbconn = sqlite3.connect('../h3db/AIAcademicBase.sqlite3')
+dbcur = dbconn.cursor()
+
+dbcur.execute(''' select name from nips_authors ''')
+rows = dbcur.fetchall()
+for row in rows:
+    print row
+
+dbconn.close()

### 2016-03-18 h3scrapem/test.rb
add test.rb for crawl

@@ -1,0 +1,41 @@
+require 'rubygems'
+require 'nokogiri'
+require 'open-uri'
+
+DATA_DIR = "data-hold"
+Dir.mkdir(DATA_DIR) unless File.exists?(DATA_DIR)
+
+BASE_WIKIPEDIA_URL = "https://en.wikipedia.org"
+LIST_URL = "#{BASE_WIKIPEDIA_URL}/wiki/List_of_Nobel_laureates"
+
+HEADERS_HASH = {"User-Agent" => "Ruby/#{RUBY_VERSION}"}
+
+page = Nokogiri::HTML(open(LIST_URL))
+rows = page.css('div.mw-content-ltr table.wikitable tr')
+
+rows[1..5].each do |row|
+  hrefs = row.css("td a").map{ |a|
+    a['href'] if a['href'] =~ /^\/wiki\//
+  }.compact.uniq
+
+  hrefs.each do |href|
+    remote_url = BASE_WIKIPEDIA_URL + href
+    puts remote_url
+    local_fname = "#{DATA_DIR}/#{File.basename(href)}.html"
+    unless File.exists?(local_fname)
+      puts "Fetching #{remote_url}..."
+      begin
+        wiki_content = open(remote_url, HEADERS_HASH).read
+      rescue Exception=>e
+        puts "Error: #{e}"
+        sleep 5
+      else
+        File.open(local_fname, 'w'){|file| file.write(wiki_content)}
+        puts "\t...Success, saved to #{local_fname}"
+      # ensure
+      #   sleep 1.0 + rand
+      end  # done: begin/rescue
+    end # done: unless File.exists?
+
+  end # done: hrefs.each
+end # done: rows.each

### 2016-03-19 ml_notes/draft.tex
update ml_notes

@@
 % the note in the first column to ``Under review.  Do not distribute.''
-\usepackage{icml2016}
+\usepackage[accepted]{icml2016}
 
@@
 %\usepackage[accepted]{icml2016}
-
 %-------------------------------------------------------------
@@
 \newcommand{\mname}{\texttt{OLCS}}
+\newcommand{\question}[1]{\textcolor{red}{Q: #1}}
+\newcommand{\lrb}{\left{\right}}
 
@@
 where $\sigma_n^2$ is the noise level and $K_{\cdot,\cdot}$ represents a shorthand for covariance matrix.
+\question{Here comes the question of how to estimate the parameters for the covariance $K$.}
 
@@
 \]
+
+\section{PCA}
+The basic idea of PCA is to maximally reduce information loss of projecting high dimensional data to lower dimension.
+Therefore, an intuitive consideration would be that we introduce first of all a projection matrix $\vct u$ on $d$-dimensional instance $x$, so that $x$ is mapped on a lower $m$-dimensional space.
+Following column vector routine, we expect that matrix $\vct u$ as being $m \times d$.
+Now given a dataset $ \vct X = \left\{  x_i\right\}_{i=1}^{n}$, it will be projected on a $ m $-dimensional space by $\vct u$.
+The objective of the projection is to maximize the covariance of data on the lower dimensional space, that is,
+\[
+	\max \dfrac{1}{n}\sum_{i=1}^{n}\|\vct ux - \vct u\bar{x}\|^2 
+\]
+that can be rewritten as,
+\begin{eqnarray}
+	& \underset{\vct u}{\textit{maximize}}\quad \vct u S \vct u^T \nonumber \\ 
+	\text{s.t.} & \vct u_i\vct u_i^T = 1, \,\, i=1,\ldots,m
+	\label{eq:pca_obj}
+\end{eqnarray}
+where $S$ is the covariance of $\vct X$. To prevent $\vct u$ goes to infinity, we assume $\vct u$ has unit length, namely, $\vct u$ represents a set of basis of the lower dimension.
+
+According to \eqref{eq:pca_obj}, we introduce $m$ Lagrangian multipliers $\vct \lambda$ as a diagonal matrix, and we have 
+\[ L = \underset{\vct u}{\textit{maximize}}\quad \vct u S \vct u^T - \vct\lambda \vct u\vct u^T \]
+
+Take the derivative of $L$ with respect to $\vct u$, we have
+\begin{eqnarray}
+	\vct uS & = & \vct\lambda\vct u \nonumber \\
+	S & = & \vct u^{-1}\lambda\vct u
+	\label{eq:pca_sol}
+\end{eqnarray}
+Since $\vct u$ is orthogonal, it is therefore not singular.
+We see that $\vct u$ and $\vct lambda$ are the indeed the eigenvectors and eigenvalues for $S$ respectively.
+And Eq.\eqref{eq:pca_sol} is exactly the singular value decomposition of $S=U\Sigma V^T$, we can derive $\vct u$ and $ \vct{\lambda} $ from $S$ conveniently.
+
 \bibliography{myrefs}

### 2016-03-22 talks/cbn-latex/sections/causalBN.tex
add talks

%% START NEW SECTION
\section{Causal Bayesian Network}
\subsection{Background and Definition}
\begin{frame}{Assumptions}
\begin{itemize}[<+->]
\item Causal Markov Condition
	\begin{itemize}
	\item Every variable is independent of its non-descendants given its parents
	\item Factorization: $P(X_1,\ldots,X_n)=\prod_iP(X_i\,|\,Parents(X_i))$
	\end{itemize}
\item Faithfulness: causal structure fully determines independences
\item Acyclic: needs to be defined in problem setting
\item Causal sufficiency
	\begin{itemize}
	\item Assume no latent common cause
	\item For efficient learning, also for causal interpretation of output
	\end{itemize}
\end{itemize}
\end{frame}
\begin{frame}{Causal Bayesian Network}
\begin{definition}
Given a set of variables ${X_1,\ldots, X_n}$, a Bayesian network is
a probabilistic graphical model $B = (\mathcal{G}, \Theta)$, where $\mathcal{G}=(V,E)$ is a
directed acyclic graph (DAG) and $\Theta$ is the set of the
parameters in all conditional probability distributions (CPDs).
\end{definition}
A Bayesian network $B$ is said to be causal when do intervention on any subset $X\subseteq V$, i.e., do(X), 
resulting in a set of interventional distributions $P_x$, denoted by $P_*$, and the following three conditions hold:
\begin{itemize}
\item $P_x$ is Markov relative to $\mathcal{G}$
\item $P_x(v_i)=1$ for all variables $v_i\in X$
\item $P_x(v_i\,|\,pa_i)=P(v_i|pa_i)$ for all variables $v_i\notin X$
\end{itemize} 
\end{frame}
\begin{frame}{An example}
\begin{figure}
\centering
\includegraphics[scale=0.4]{imgs/bnexample}
\end{figure}
\end{frame}
\subsection{Learning Bayesian Network}
\begin{frame}{Problem Setting}
\begin{block}{Goal}
Given a dataset $\mathcal{D}$, try to learn the graph $\mathcal{G}$ and the
parameters of all conditional probability distribution $\Theta$.
\end{block}\pause
\begin{itemize}
\item[] \textbf{Traditional method}
	\item First step: structure learning
	\item Second step: parameter estimation conform to the inferred structure 
\end{itemize}
\end{frame}
\begin{frame}{Structure learning}
\begin{columns}
\begin{column}[t]{5cm}
\textbf{Constraint based}\\
Run conditional independence tests in 
data and find a DAG faithful to 
them. 
\begin{itemize}
\item \textit{Methods:} SGS, PC, TPDA, CPC 
\end{itemize}
\textbf{Hybrid}\\
Combining both constraint based and score based.
\begin{itemize}
\item \textit{Methods:} MMHC, CB, ECOS
\end{itemize}
\end{column}
\begin{column}[t]{5cm}
\textbf{Score based}\\
Find a DAG by maximizing the
posteriori probability given the data.
\begin{itemize}
\item \textit{Methods:} K2, Sparse Candidate, GBPS, BIC/AIC
\end{itemize}
\end{column}
\end{columns}
\end{frame}
\begin{frame}{Parameter Estimation}
Given the structure $\mathcal{G}$ learned from last step, factorization
will be applied according to local terms governed by parameters $\theta_i$
\begin{center}
$P(X_1,\ldots,X_n)=\prod_iP(X_i\,|\,Pa_i, \theta_i)$
\end{center}
Any parameter estimator will work here, e.g, MLE, MAP
\end{frame}
\begin{frame}{Some problems in BN Learning}
\begin{itemize}
\item Search space is exponentially large in high dimension
\item Too many conditional tests
\item Local minimum
\item Parametric form needed
\item Missing values
\item Latent variables
\item Hybrid node type
\end{itemize}
\end{frame}

### 2016-03-22 talks/cbn-latex/sections/copulaLearn.tex
add talks

\section{A Copula-based Learning Approach}
\subsection{Copula theory}
\begin{frame}{Copula functions}
\begin{definition}
Let $U_1,\ldots,U_N$ be real random variables marginally uniformly distributed over $\left[0,1\right]$. A Copula function C is a cumulative joint probability function: $\left[0,1\right]^N \rightarrow \left[0,1\right]$.
\[
C\left(u_1,\ldots ,u_N\right)=P\left(U_1\leq u_1,\ldots ,U_N\leq u_N\right)
\]
\end{definition}	
A Copula function $C$ can be viewed as a probability function of points
distribution in a $N$-dimensional unit hypercube.
\end{frame}
\begin{frame}{Sklar's theorem}
Copula function is important because of the Sklar's theorem
\begin{theorem}[Sklar 1959]
Let $F\left(x_1,\ldots,x_N\right)$ be any cumulative multivariate distribution over real-valued random variables, then there exists a copula function $C$ such that
\begin{center}
$F\left(x_1,\ldots,x_N\right) = C\left(F\left(x_1\right),\ldots,F\left(x_N\right)\right)$,
\end{center}
where $F\left(X_i\right)$ is marginal cumulative density distribution
of variable $X_i$ and furthermore if each $F\left(X_i\right)$ is continuous then the Copula is unique.
\end{theorem}
\end{frame}
\begin{frame}{Copula Multivariate Modelling}
\textbf{Advantages}
\begin{itemize}
\item Total independent free choice of marginal distributions
\item Ability of transforming any joint distribution into a specific parametric form
\item Decrease the number of paramters to be estimated dramatically 
\item Non-parametric estimators are allowed on marginals
\end{itemize}\pause
\textbf{Multivariate modelling by Copula functions}
\begin{enumerate}[<+->]
\item Finding univariate marginals via either parametric or non-parametric ways
\item Defining a Copula function to capture the dependence structure of model
\end{enumerate}
\end{frame}
\begin{frame}{Gaussian Copulas}
\textbf{Gaussian Copula} is a widely used Copula function because of its extensive practical importance in many fields and also for computational simplicity. It has the form as follows: 
\begin{center}
$C\left(\left\lbrace F\left(x_i\right)\right\rbrace\right) = \Phi_\Sigma\left(\phi^{-1}\left(F\left(x_1\right)\right),\ldots,\phi^{-1}\left(F\left(x_n\right)\right)\right)$
\end{center}
where $\phi$ is standard normal distribution, $\Phi_\Sigma$ is zero mean normal distribution with correlation matrix $\Sigma$. \\
Other Copulas like Archimedean Copulas, Clayton Copulas, Vine Copula Models are also well studied.
\end{frame}
\begin{frame}{Gaussian Copulas, ctd.}
Taking the $N$-th order derivatives of $C$, we obtain the Gaussian Copula density function $c\left(\left\lbrace F\left(x_i\right)\right\rbrace\right)= $
\begin{align*}
\frac{1}{\sqrt{det\Sigma}}exp\left(-\frac{1}{2} \begin{pmatrix}
\phi^{-1}\left(F\left(x_1\right)\right)\\
\vdots\\
\phi^{-1}\left(F\left(x_N\right)\right)
\end{pmatrix}^T \left(\Sigma^{-1}-\mathbf{I}\right)\begin{pmatrix}
\phi^{-1}\left(F\left(x_1\right)\right)\\
\vdots\\
\phi^{-1}\left(F\left(x_N\right)\right)
\end{pmatrix}\right)
\end{align*}
where $\mathbf{I}$ is the identity matrix. Using Sklar's theorem, the multivariate Gaussian density distribution can be obtained. In a learning scheme, the correlation matrix $\Sigma$ is the only parameters to be estimated when univariate marginals are known from data observations. 
\end{frame}
\subsection{Gaussian Copula Bayesian Network}
\begin{frame}{Conditional Copula Density Function}
Let $x$ denote a variable and $\mathbf{y}=\{y_1,\dots ,y_k\}$ are the parents of $x$. And $f(x\,|\,\mathbf{y})$ is the conditional density function and $f(x)$ denotes the marginal density of $x$. And there exists a Copula density function $c(F(x),F(y_1),\dots ,F(y_k))$ such that: 
\[
f(x|\mathbf{y})=R_c(F(x),F(y_1),\dots , F(y_k))
\]
where $R_c$ is the Copula ratio
\begin{align*}
R_c(F(x),F(y_1),\dots , F(y_k))& \equiv \frac{c(F(x),F(y_1),\dots , F(y_k))}{\int c(F(x),F(y_1),\dots , F(y_k))f(x)dx}\nonumber\\
& =\frac{c(F(x),F(y_1),\dots , F(y_k))}{\frac{\partial^kC(1,F(y_1),\dots ,F(y_k))}{\partial F(y_1)\dots \partial F(y_k)}}
\end{align*}
and $R_c$ is defined to be 1 when $\mathbf{y}=\emptyset$. 
\end{frame}
\begin{frame}{Factorization of Copulas}
Consider again the factorization of Bayesian network: $p\left( X\right) = \prod^m_{i=1}p(x_i\,|\,\mathbf{Pa_i})$\\
Copulas can be decomposed in a similar way: 
\begin{block}{Decomposition of Copulas}
Given a directed acyclic graph $\mathcal{G}$ encoding conditional independences over $\mathcal{X}$, the Copula density $c\left(F\left(x_1\right),\ldots, F\left(x_N\right)\right)$ can also be decomposed according to $\mathcal{G}$
\[
c\left(F\left(x_1\right),\ldots, F\left(x_N\right)\right) = \prod_i R_{c_i}(F(x_i),\left\lbrace F(\mathbf{Pa_{ik}})\right\rbrace) 
\]
\end{block}
where $c_i$ is the local Copula ratio on variable $x_i$
\end{frame}
\begin{frame}{Copula Bayesian Network Model}
\begin{definition}
A Copula Bayesian Network (CBN) is a triplet $\mathcal{C}=(\mathcal{G}, \Theta_C, \Theta_f)$ encoding the joint density $f_\mathcal{X}(x)$. $\Theta_C$ is a set for all local Copula densities $c_i(F(x_i),\left\lbrace F(\mathbf{Pa_{ik}})\right\rbrace)$ and $\Theta_f$ is the set of parameters representing the univariate marginals $f(x_i)$. Then $f_\mathcal{X}(x)$ can be parameterized as
\[
f_\mathcal{X}(x)=\prod_i R_{c_i}(F(x_i),\left\lbrace F(\mathbf{Pa_{ik}})\right\rbrace)f(x_i)
\]
\end{definition}
By sharing the global univariate marginals, the hypothesis space on parameters has been largely reduced.
\end{frame}
\subsection{Learning Copula Bayesian Network}
\begin{frame}{Parameter Estimation}
In the case of Gaussian Copula, and we take the MLE method given data observations $T$. The log-likelihood can be written as:
\begin{equation*}
\ell(\theta) = \sum^{|T|}_{t=1}\ln c(F_1(x_1^t;\theta_1), \cdots ,F_N(x_N^t;\theta_N),\alpha)+\sum^{|T|}_{t=1}\sum^N_{n=1}\ln f_n(x^t_n;\theta_n)
\end{equation*}
where $\theta_i$ is the parameters of marginal distribution $x_i$ and $\alpha$ is the set of parameters governing the dependencies.
\end{frame}
\begin{frame}{Structure Learning}
For structure learning, we use the partial inverse correlation matrix (PICM) method (constraint based).\\
\textbf{Basic idea:} simply inverse the estimated covariance matrix $\Sigma$ in Gaussian Copula, and scale the diagonals as $1$.
\begin{small}
\onslide<2->{$\Sigma^{-1} =
\begin{pmatrix}
s_{1,1} & s_{1,2} & \cdots & s_{1,n} \\
s_{2,1} & s_{2,2} & \cdots & s_{2,n} \\
\vdots   & \vdots   & \ddots & \vdots \\
s_{n,1} & s_{n,2} & \cdot & s_{n,n} \\
\end{pmatrix}$}
\onslide<3->{$\xRightarrow{scale}
\begin{pmatrix}
1 & \frac{s_{1,2}}{s_{1,1}*s_{2,2}} & \cdot & \frac{s_{1,n}}{s_{1,1}*s_{n,n}} \\[0.3em]
\frac{s_{2,1}}{s_{2,2}*s_{1,1}} & 1 & \cdot & \frac{s_{2,n}}{s_{2,2}*s_{n,n}} \\[0.3em]
\vdots   & \vdots   & \ddots & \vdots \\
\frac{s_{n,1}}{s_{n,n}*s_{1,1}} & \frac{s_{n,2}}{s_{n,n}*s_{2,2}} & \cdot & 1 \\
\end{pmatrix}$}
\end{small}\\[0.5em]
\onslide<4->{\alert{If $\frac{s_{i,j}}{\sqrt{s_{i,i}*s_{j,j}}} \leq \sigma (\text{very small}) \Rightarrow X_i \ci X_j \,|\, \left\lbrace X_{q\neq i,j} \right\rbrace$}}
\end{frame}
\begin{frame}{PICM to Moral Graph}
A zero-entry in PICM implies no direct edge between two variables, we construct a moral graph accordingly, e.g., 
\begin{figure}
\setcounter{subfigure}{0}
\begin{subfigure}[H]{0.4\textwidth}
\includegraphics[scale=0.4]{imgs/BNs7n}
\caption{Original DAG}
\end{subfigure}\hfill $\Rightarrow$ \hfill
\begin{subfigure}[H]{0.4\textwidth}
\includegraphics[scale=0.4]{imgs/BNs7nMoral}
\caption{Moral graph}
\end{subfigure}
\end{figure}
\textbf{Moral} is a term known as the married edge of the parents for a collider (two nodes converge at a common node, i.e., non-equivalence ).
\end{frame}
\begin{frame}{Detriangulation of Moral Graph}
\textbf{Note} that the additional dependences are brought by colliders (see nodes C, F, and G) and by conditioned on colliders, dependences will disappear, namely, $A\dep B \, | \, C$ but $A\ci B \,|\, \emptyset$. This motivates us to remove those additional dependences (married edges).\pause
\begin{figure}
\setcounter{subfigure}{0}
\begin{subfigure}[H]{0.4\textwidth}
\includegraphics[scale=0.4]{imgs/BNs7nMoral}
\caption{Moral graph}
\end{subfigure}\hfill $\Rightarrow$ \hfill
\begin{subfigure}[H]{0.4\textwidth}
\includegraphics[scale=0.4]{imgs/BNs7nDet}
\caption{Partially directed graph after removing moral edges}
\end{subfigure}
\end{figure}
\end{frame}
\begin{frame}{Contraint Propagation (Judea Pearl 2000)}
Constraints: Colliders, Acyclicity
 \begin{figure}[H]
  \centering
  \hfill\includegraphics[width=0.4\textwidth]{imgs/R1}%      
  \hfill\includegraphics[width=0.4\textwidth]{imgs/R2}\hspace*{\fill}\newline
  \vspace{0.5mm}
  \hspace*{\fill}\includegraphics[width=0.4\textwidth]{imgs/R3}%
  \hfill\includegraphics[width=0.4\textwidth]{imgs/R4}\hspace*{\fill}
  \caption{Rules for completion of orientations}
 \end{figure}
\end{frame}
\begin{frame}{Maximally Oriented Acyclic Graph}
Recursively propagate constraints, we obtain a maximally oriented acyclic graph (\alert{only equivalence class})
\begin{figure}
\setcounter{subfigure}{0}
\begin{subfigure}[H]{0.4\textwidth}
\includegraphics[scale=0.4]{imgs/BNs7nDet}
\caption{Partially directed graph after removing moral edges}
\end{subfigure}\hfill $\Rightarrow$ \hfill
\begin{subfigure}[H]{0.4\textwidth}
\includegraphics[scale=0.4]{imgs/BNs7n}
\caption{Maximally oriented acyclic graph}
\end{subfigure}
\end{figure}
\end{frame}

### 2016-03-22 talks/cbn-latex/sections/fundamental.tex
add talks

\section{Fundamental of Causal Inference}
\subsection{Motivation}
\begin{frame}{What is Causality?}
\begin{block}{A definition from Wikipedia}
\textbf{Causality} (also referred to as causation) is the relationship
between an event (\textit{the cause}) and a second event (\textit{the effect}),
where the second event is understood as a consequence of the
first.
\end{block}\pause
\textbf{An example in real life} : Does smoking cause lung cancer?\\
\pause	
\begin{center}
\alert{Yes, it might be!}
\end{center}
\end{frame}
\begin{frame}{From Probabilistic View }
\textbf{Problem:} Does smoking cause lung cancer?\pause
\begin{center}
\begin{itemize}
\item Smoking does \alert{increase the probability} of getting lung cancer.
\end{itemize}
\end{center}
\end{frame}
\begin{frame}{Statistical Inference Overview}
\begin{figure}
\includegraphics[scale=0.7]{imgs/statInf}
\end{figure}
\begin{itemize}
\item Approximate an estimate of $X$ given evidence $e$, namely, $Pr(X\,|\,e)$. E.g., Regression or Classification problems.
\item Rejection of hypothesis, i.e., assert wether samples are from a certain distribution.  
\item Confidence interval, i.e., construct an interval based on dataset 
\end{itemize}
\end{frame}
\begin{frame}{Causal Inference Overview}
\begin{figure}
\includegraphics[scale=0.6]{imgs/causalInf}
\end{figure}
\begin{itemize}
\item What if $P$ has shifted itself to $P^*$?
\item<2-> \textbf{Key factors:} Causes, Changes, and Invariants . 
\item<2-> Inference of $P^*$ and reasoning of changes. 
\end{itemize}
\end{frame}
\begin{frame}{What makes Causal Inference interesting?}
\begin{itemize}
\item Human understands the world in terms of causes and effects.
\item Empirical science is about establishing causes.
\item Causal inference gives a mathematical language for causal
statements, and tools to solve causal problems formally.
\item Alternative exercising to decision making, reasoning, etc.
\end{itemize}
%\begin{alertblock}{Note}
%Causal Inference has fundamental difference with machine learning
%\end{alertblock}
\end{frame}
\subsection{Causal Graphical Model}
\begin{frame}{Association}
\begin{itemize}
\item Now we want to find out what \alert{causes} lung cancer
\end{itemize} \pause
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
& & \multicolumn{2}{|c|}{Lung cancer}\\\hline
smoking & yellow teeth & yes & no\\\hline
yes & yes & 100 & 400\\\hline
yes & no & 100 & 400\\\hline
no & yes & 1 & 450\\\hline
no & no & 9 & 8540\\\hline
\end{tabular}
\caption{Data observations from 10000 people}
\end{table}
\end{column}\hfill
\begin{column}{0.5\textwidth}
\vspace*{-0.5in}
\begin{figure}
\centering
\includegraphics[scale=0.6]{imgs/smokepl}
\end{figure}
\end{column}
\end{columns}
\end{frame}
\begin{frame}{Measurements of Association}
\textbf{To find out associations among variables}
\begin{itemize}
\item Mutual information (Information theory)
\item Pearson (linear) correlation
\item Spearman's rho (rank correlation)
\item Effect size between two variables
\item Many others
\end{itemize}
\end{frame}
\begin{frame}{Observations from Data}
\textbf{Obviously}
\begin{itemize}
\item \textit{yellow teeth} and \textit{lung cancer} are associated.
\end{itemize}\pause
\alert{\textbf{But...}}
\begin{itemize}
\item Bleaching the teeth does not help reduce the probability
of getting lung cancer.
\end{itemize}\pause
\begin{alertblock}{Caution!}
Correlation does not imply Causation
\end{alertblock}
\end{frame}
\begin{frame}{Statistical Implication}
\begin{block}{Reichenbach's \textit{Common Cause Principle}}
If $X$ and $Y$ are correlated, then either $X$ causes $Y$ or $Y$ causes $X$ or they share a latent common cause $Z$.
\end{block}
\begin{figure}
\setcounter{subfigure}{0}
	\centering
	\begin{subfigure}[H]{0.3\textwidth}
		\centering
		\includegraphics[scale=0.3]{imgs/x2y}
		\caption{$X$ causes $Y$}
		%\label{}	
	\end{subfigure}
	\begin{subfigure}[H]{0.3\textwidth}
		\centering
		\includegraphics[scale=0.3]{imgs/y2x}
		\caption{$Y$ causes $X$}
		%\label{}	
	\end{subfigure}
	\begin{subfigure}[H]{0.3\textwidth}
		\centering
		\includegraphics[scale=0.3]{imgs/z2xy}
		\caption{A common latent cause $Z$}
		%\label{}	
	\end{subfigure}
\end{figure}\pause
\begin{itemize}
\item<+-|alert@+> It links causality with probability
\end{itemize}
\end{frame}
\begin{frame}{Functional Causal Model (pearl et al.)} 
\begin{itemize}[<+->]
\item A set of variables (factors) $\left\lbrace X_1,\ldots,X_n \right\rbrace$
\item Directed acyclic graph $\mathcal{G}$ with vertices $\left\lbrace X_1,\ldots,X_n \right\rbrace$
\item Parents of node $X_i$ in $\mathcal{G}$ are its direct causes
\item $X_i=f_i(Parents(X_i),\epsilon_i)$, where $\left\lbrace\epsilon_1,\ldots,\epsilon_n\right\rbrace$ are jointly independent noises
\item The above entails a joint probability distribution $P(X_1,\ldots,X_n)$
\item Problems are twofold:
      \begin{enumerate}
		\item How is the $P$ like?
		\item Can we recover $\mathcal{G} from P$? 
	\end{enumerate}
\item[] \begin{textblock*}{200mm}(0.6\textwidth,-2cm)
		\includegraphics[scale=0.25]{imgs/causalgm}
	\end{textblock*}
\end{itemize}
\end{frame}
\begin{frame}{Functional Causal Model, ctd.}
The following are equivalent:
\begin{itemize}
\item A functional causal model exists
\item Local causal Markov condition: $X_i$ is statistically independent of its non-descendants given $X_i$'s parents
\item Global Causal Markov condition: \textbf{d-separation} characterize the set of independences over all the observables
\item Factorization: $P(X_1,\ldots,X_n)=\prod_iP(X_i\,|\,Parents(X_i))$
\end{itemize}
\end{frame}
\begin{frame}{Learning causation from Data?}
\begin{block}{Question}
Given observational data, can we infer $\mathcal{G}$?
\end{block}
\begin{itemize}
\item \textbf{Simple answer:} impossible without additional information
\item Possible with interventions (outside force, empirical treatment, etc.)
\item By conditional independence tests, \textit{Markov equivalence class} containing $\mathcal{G}$ can be learned. \alert{But}, it fails in simplest 2-nodes case.
\item 2-nodes case can be tackled applying residual dependence test. (see Hoyer et al.)
\end{itemize}
\end{frame}
\begin{frame}{Markov Equivalence Class}
\textbf{Simplest case with three variables}
\begin{itemize}
\item[]<1-> \begin{figure}
\setcounter{subfigure}{0}
			\begin{subfigure}[H]{0.4\textwidth}
			\includegraphics[scale=0.4]{imgs/eqv}
			\caption{Equivalence}
			\end{subfigure}\hfill
			\begin{subfigure}[H]{0.3\textwidth}
			\includegraphics[scale=0.4]{imgs/noneqv}
			\caption{Non-equivalence}
			\end{subfigure}
		\end{figure}
\item<2-> Samples can be explained by all graphs in equivalence class
\item<3-> For example:
\begin{table}
\centering
\begin{tabular}{|c|c|}
\hline
Equivalence class & Non-equivalence class \\\hline
$Dep(X,Z\,|\,\emptyset)$ & $Dep(X,Z\,|\,\emptyset)$\\\hline
$Dep(Y,Z\,|\,\emptyset)$ & $Dep(Y,Z\,|\,\emptyset)$\\\hline
$Dep(X,Y\,|\,\emptyset)$ & \alert{$Ind(X,Y\,|\,\emptyset)$}\\\hline
$Ind(X,Y\,|\,Z)$ & \alert{$Dep(X,Y\,|\,Z)$}\\\hline
\end{tabular}
\end{table}	
\end{itemize}
\end{frame}

### 2016-03-22 talks/cbn-ppt-internal/cbn.tex
add talks

\documentclass{beamer}
\usepackage{amsmath,amsfonts}	% use math symbols
\usepackage{graphicx} % insert images
\usepackage{url} % insert urls
\usepackage{textpos} % package for the positioning
\usetheme{Ilmenau} % change theme

\begin{document}

%% MAKE TITLE
\title{Basic Beamer Template}
\subtitle{A subtitle should be placed here}
\author{Huang Xiao} %\\ \small{xiaohu@in.tum.de} }%\thanks{Funded by ARAMiS project}}
%\and Author2 \inst{1} }
%\and Author3 \inst{2}}
\institute[Technische Universit\"at M\"unchen]
{ 
	%\inst{1} 
	Chair of IT Security (I20) \\Department of Informatics \\Technische Universit\"at M\"unchen 
	%\and
	%\inst{2} Cloud Service Lab\\Fraunhofer AISEC
}

\date{\today}
\maketitle

%% CHANGE THE DEFAULT TEMPLATE
% position the logo
\addtobeamertemplate{frametitle}{}{%
\begin{textblock*}{100mm}(0.98\textwidth,-0.7cm)
\includegraphics[height=0.53cm,width=0.9cm,keepaspectratio]{imgs/TUM}
\end{textblock*}}

\AtBeginSection[] {
	\frame<beamer>{ 
		\frametitle{Overview}   
		\tableofcontents[currentsection] 
 	}
 }
 % add frame number
%\setbeamertemplate{footline}{%
  %\raisebox{5pt}{\makebox[\paperwidth]{\hfill\makebox[10pt]{\scriptsize\insertframenumber}}}}

%% START PRESENTATION
\section{Introduction}

\begin{frame}{Introduction}

\begin{itemize}
\item Define the problem being studied.
\item Explain your interest in the problem.
\item Outline how the problem is to be investigated.
\end{itemize}

\end{frame}
\subsection{XXX1}
\begin{frame}{xxx1}

\begin{itemize}
\item Define the problem being studied.
\item Explain your interest in the problem.
\item Outline how the problem is to be investigated.
\end{itemize}

\end{frame}
\subsection{XXX2}
\begin{frame}{xxx2}

\begin{itemize}
\item Define the problem being studied.
\item Explain your interest in the problem.
\item Outline how the problem is to be investigated.
\end{itemize}

\end{frame}

\section{History}

\begin{frame}{History}

\begin{itemize}
\item Discuss the history of the problem.
\item Describe context for the problem.
\item Outline prior work on the problem.
\end{itemize}

\end{frame}

\section{Representation}

\begin{frame}{Representation}

Represent the problem in symbolic, graphic, or numeric format.

\bigskip

Mathematical formulas may be typeset:
\[ \int_0^\frac{\pi}{2}\frac{1+\cos 2x}{2} \: dx \]

\end{frame}

\section{Methods}

\begin{frame}{Methods and Tools}

Discuss technical methods or tools required to formulate and solve the problem mathematically.

\bigskip

\begin{theorem}
If $f$ is continuous on $[a,b],$ then
$$\int_{a}^{b} f(x) \: dx = F(b) - F(a)$$
where $F$ is any antiderivative of $f,$ that is, a function such that $F' = f.$
\end{theorem}

\end{frame}

\section{Solution}

\begin{frame}{Solution of the Problem}

Present a solution of the problem, perhaps for a simple case, and indicate how the solution may be achieved in other cases.

\bigskip

\begin{example}
\[ \int_0^\frac{\pi}{2}\frac{1+\cos 2x}{2} \: dx=\frac{\pi}{4}  \]
\end{example}

\end{frame}

\section{Conclusion}

\begin{frame}{Conclusion}

Summarize the information presented in the talk.

\bigskip

\begin{itemize}
\item Problem statement
\item Relevance
\item Mathematical tools
\item Solution
\end{itemize}

\end{frame}

\section{References}

\begin{frame}{References}

\begin{thebibliography}{99}
\bibitem{Boas} R. P. Boas,  Can we make mathematics intelligible?  \textit{Amer. Math. Monthly}, \textbf{88} (1981), 727--731.

\bibitem{Page} M. E. Page,  A Brief Citation Guide for Internet Sources in History and the Humanities (Version 2.1),
\begin{url}http://h-net.msu.edu/$\sim$africa/citation.html\end{url}.

\end{thebibliography}

\end{frame}

\end{document}

### 2016-03-22 talks/templates/tum-beamer/cbn2012.tex
add talks

--- 2016-03-22 talks/cbn-ppt-internal/cbn.tex
@@
 %% MAKE TITLE
-\title{Basic Beamer Template}
-\subtitle{A subtitle should be placed here}
+\title{Learning from Causation}
+\subtitle{Fundamental of Casual Inference and its Applications}
 \author{Huang Xiao} %\\ \small{xiaohu@in.tum.de} }%\thanks{Funded by ARAMiS project}}
@@
 %% START PRESENTATION
-\section{Introduction}
-
-\begin{frame}{Introduction}
-
+\section{Fundamental of Causal Inference}
+\subsection{Motivation}
+\begin{frame}{What is Causality?}
+\begin{block}{A definition from Wikipedia}
+\textbf{Causality} (also referred to as causation) is the relationship
+between an event (\textit{the cause}) and a second event (\textit{the effect}),
+where the second event is understood as a consequence of the
+first.
+\end{block}\pause
+\textbf{An example in real life} : Does smoking cause lung cancer?\\
+\pause	
+\begin{center}
+\alert{Yes, it might be!}
+\end{center}
+\end{frame}
+\begin{frame}{From Probabilistic View }
+\textbf{Problem:} Does smoking cause lung cancer?\pause
+\begin{center}
 \begin{itemize}
-\item Define the problem being studied.
-\item Explain your interest in the problem.
-\item Outline how the problem is to be investigated.
+\item Smoking does \alert{increase the probability} of getting lung cancer.
 \end{itemize}
-
+\end{center}
 \end{frame}
-\subsection{XXX1}
-\begin{frame}{xxx1}
-
+\begin{frame}{Statistical Inference Overview}
+\begin{figure}
+\includegraphics[scale=0.7]{imgs/statInf}
+\end{figure}
 \begin{itemize}
-\item Define the problem being studied.
-\item Explain your interest in the problem.
-\item Outline how the problem is to be investigated.
+\item Approximate an estimate of $X$ given evidence $e$, namely, $Pr(X\,|\,e)$. E.g., Regression or Classification problems.
+\item Rejection of hypothesis, i.e., assert wether samples are from a certain distribution.  
+\item Confidence interval, i.e., construct an interval based on dataset 
 \end{itemize}
-
 \end{frame}
-\subsection{XXX2}
-\begin{frame}{xxx2}
-
+\begin{frame}{Causal Inference Overview}
+\begin{figure}
+\includegraphics[scale=0.6]{imgs/causalInf}
+\end{figure}
 \begin{itemize}
-\item Define the problem being studied.
-\item Explain your interest in the problem.
-\item Outline how the problem is to be investigated.
+\item What if $P$ has shifted itself to $P^*$?
+\item<2-> \textbf{Key factors:} Causes, Changes, and Invariants . 
+\item<2-> Inference of $P^*$ and reasoning of changes. 
 \end{itemize}
-
 \end{frame}
-
+\begin{frame}{What makes Causal Inference interesting?}
+\begin{itemize}
+\item Human understands the world in terms of causes and effects.
+\item Empirical science is about establishing causes.
+\item Causal inference gives a mathematical language for causal
+statements, and tools to solve causal problems formally.
+\item Alternative exercising to decision making, reasoning, etc.
+\end{itemize}
+%\begin{alertblock}{Note}
+%Causal Inference has fundamental difference with machine learning
+%\end{alertblock}
+\end{frame}
+\subsection{Causal Graphical Model}
+\begin{frame}{Association}
+\begin{itemize}
+\item Now we want to find out what \alert{causes} lung cancer
+\end{itemize} \pause
+\begin{columns}
+\begin{column}{0.5\textwidth}
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+& & \multicolumn{2}{|c|}{Lung cancer}\\\hline
+smoking & yellow teeth & yes & no\\\hline
+yes & yes & 100 & 400\\\hline
+yes & no & 100 & 400\\\hline
+no & yes & 1 & 450\\\hline
+no & no & 9 & 8540\\\hline
+\end{tabular}
+\caption{Data observations from 10000 people}
+\end{table}
+\end{column}\hfill
+\begin{column}{0.5\textwidth}
+\vspace*{-0.5in}
+\begin{figure}
+\centering
+\includegraphics[scale=0.6]{imgs/smokepl}
+\end{figure}
+\end{column}
+\end{columns}
+\end{frame}
+\begin{frame}{Measurements of Association}
+\textbf{To find out associations among variables}
+\begin{itemize}
+\item Mutual information (Information theory)
+\item Pearson (linear) correlation
+\item Spearman's rho (rank correlation)
+\item Effect size between two variables
+\item Many others
+\end{itemize}
+\end{frame}
+\begin{frame}{Observations from Data}
+\textbf{Obviously}
+\begin{itemize}
+\item \textit{yellow teeth} and \textit{lung cancer} are associated.
+\end{itemize}\pause
+\alert{\textbf{But...}}
+\begin{itemize}
+\item Bleaching the teeth does not help reduce the probability
+of getting lung cancer.
+\end{itemize}\pause
+\begin{alertblock}{Caution!}
+Correlation does not imply Causation
+\end{alertblock}
+\end{frame}
+%% START NEW SECTION
 \section{History}

### 2016-03-22 talks/writtings/forsec_huang.tex
add talks

\documentclass{llncs}
\usepackage[absolute]{textpos}
\usepackage{times}
\usepackage{float}
\usepackage{dsfont}
\usepackage{upgreek}
\usepackage[hang,tight]{subfigure}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
%\usepackage{txfonts}
% \usepackage{mathrsfs}
%\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{pstricks, multido, pst-plot, epsfig, pst-grad}
\usepackage{multirow}
%\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
%\usepackage{algorithmicx}
%\usepackage{algpseudocode}
%\usepackage[section]{algorithm}
\usepackage{breqn}
\usepackage{hyperref}
\usepackage[capitalise]{cleveref}
\usepackage[nodisplayskipstretch]{setspace}
\AtBeginDocument{%
  \addtolength\abovedisplayskip{-0.5\baselineskip}%
  \addtolength\belowdisplayskip{-0.5\baselineskip}%
  \addtolength\abovedisplayshortskip{-0.5\baselineskip}%
  \addtolength\belowdisplayshortskip{-0.5\baselineskip}%
}
%\allowdisplaybreaks
% \crefname{algocf}{Algorithm}{Algorithms}
% \Crefname{algocf}{Algorithm}{Algorithms}
% \crefformat{equation}{(#2#1#3)}
% \Crefformat{equation}{(#2#1#3)}

%\let\chapter\undefined %fix a bug in <algorithm2e>
%\dontprintsemicolon
% \SetAlFnt{\scriptsize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TO BE REMOVED IN FINAL VERSION %%
\usepackage{ifthen}
\usepackage{color}
\newboolean{ShowComments}
\setboolean{ShowComments}{true}
\ifthenelse{\boolean{ShowComments}}{
 \newcommand{\mycomment}[1]{\colorbox{red}{COMMENT}\footnote{\textcolor{red}{\uppercase{{#1}}}}}
 }{\newcommand{\mycomment}[1]{}}
\let\oldhat\hat
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\mat}[1]{\mathbf{{#1}}}
\newcommand{\myrm}[1]{^{\mathrm{#1}}}
\newcommand{\myit}[1]{^{\langle #1 \rangle}}
\newcommand{\mac}[2]{\mbox{MAC}({#1},{#2})}
\newcommand{\imac}[2]{\mbox{IMAC}({#1},{#2})}
\newcommand{\eimac}[2]{\epsilon\mbox{-IMAC}({#1},{#2})}
\renewcommand{\hat}[1]{\widehat{\mathbf{#1}}}
\newcommand{\RXi}{\mathrm{\epsilon}}
\newcommand{\mytilde}[1]{\widetilde{\mathbf{#1}}}
\newcommand{\myre}{\nonumber\\}
\newcommand{\mysp}{\,\,\,}
\newcommand{\xA}{\vec{y}\myrm{m}}
\newcommand{\cK}{\mathcal{K}}
\newcommand{\mvol}{\mathrm{vol}}
\newcommand{\mexp}{\mathbb{E}}
\newcommand{\mcov}{\mathbb{C}}
\newcommand{\lexp}[1]{\langle{#1}\rangle}
\newcommand{\nd}{\mathcal{N}}
\newcommand{\vpl}[1]{#1^{\top}#1}
\newcommand{\vpr}[1]{#1#1^{\top}}
\newcommand{\vplc}[2]{#1^{\top}#2#1}
\newcommand{\vprc}[2]{#1#2#1^{\top}}
\newcommand{\kel}[2]{k(\vec{x}_{#1},\vec{x}_{#2})}
\newcommand{\kdel}[3]{k_{#3}(\vec{x}_{#1},\vec{x}_{#2})}
\newcommand{\df}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\mub}{\boldsymbol{\mu}}
\newcommand{\kab}{\boldsymbol{\kappa}}
\newcommand{\psib}{\boldsymbol{\psi}}
\newcommand{\epsb}{\boldsymbol{\epsilon}}
\newcommand{\xib}{\boldsymbol{\xi}}
\newcommand{\deltab}{\boldsymbol{\delta}}
\newcommand{\avgy}{\overline{\vec{y}}_{:,m,d}}
\newcommand{\vone}{\mathds{1}}
\newcommand{\sigb}{\boldsymbol{\sigma}}
\newcommand{\thb}{\boldsymbol{\Theta}}
\newcommand{\diag}[1]{\mathrm{diag}\left( {#1} \right)}
\newcommand{\id}[1]{\mathrm{d}{#1}}
\newcommand{\ceq}{=}%{\coloneq}
\newcommand{\tgp}{Gaussian process }
\newcommand{\han}[1]{{\color{red}#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% if > page limits, use this %%
% \usepackage[normaltitle, normalbib, normalmargins, normalsections]{savetrees}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \usepackage[hypertexnames=true,dvipdfm,pdfstartview=FitH,bookmarks=true,bookmarksnumbered=true,bookmarksopen=true
% hyperfigures,hyperindex,hypertexnames,citebordercolor={0 1
% 0},colorlinks=false,linkcolor=red,anchorcolor=blue,citecolor=green]{hyperref}
%%use this command if you want to input CJK characters
% \usepackage{CJK}
\renewcommand{\labelenumi}{\arabic{enumi})}

\begin{document}

\title{Research proposal for FORSEC} 
\author{Huang Xiao} %\and Claudia Eckert}
\institute{Institute of Informatics\\
  Technische Universit\"at M\"unchen, Germany\\
  \email{xiaohu@in.tum.de}}
  %\email{claudia.eckert@sec.in.tum.de}}
\maketitle
\vspace{20mm}
\begin{abstract}
  A collection of research lines proposed by Huang Xiao.
\end{abstract}
\section{Robust Anomaly Detection in Mobile Devices}

The diverse and evolvable characteristics of anomalies in various scenarios prohibits the homogeneous development of a detection framework. For instance in the mobile devices, the rapid growth of different applications and services  always comes along with a portion of novel attempts to compromise corresponding assets. The anomaly detectors can either neglect their existences or overreact to invoke false alarms on legitimate activities. Especially, mobile devices are highly correlated with users' own behaviors which requires that the robustness of the anomaly detection can bear the environmental complexity.

In this line of research, we concentrate on the complicate data patterns and also the essentials of state-of-art anomaly detection techniques \cite{horn01,kim11}, from which we develop a robust adaptation for mobile device. One possible application would be the secure payment transaction monitoring service. It monitors every payment transaction from the mobile device to prevent the unexpected financial loss. Instead of detecting the anomalies based on the payment information only, a robust detector also relies on the side information, such as the calendar, recent phone calls and also the supervision of user himself. The side information facilitates the monitoring routine to achieve its robustness.

\bibliography{./paper}
\bibliographystyle{plain}

\end{document}

### 2016-03-22 talks/iSVC/SVC_toolbox/svc.m

@@ -1,0 +1,156 @@
+function model=svc(data,options)
+%==========================================================================
+% Support Vector Clustering Algorithms          
+%==========================================================================  
+%   
+% Note that my codes are based on Statistical Pattern Recognition Toolbox 
+% (stprtool). See Ref. 5.
+% It should be needed to install stprtool at first. 
+%
+% Input:
+%   data [struct] Training data:
+%       .X [dim x num_data] Training input vectors.
+%       .y [1 x num_data] Output cluster labels
+%  X [dim x num_data] Input data.
+%  options [struct] Control parameters:
+%   .ker [string] Kernel identifier (default 'linear'). See 'help kernel'.
+%   .arg [1 x nargs] Kernel arguments.
+%   .C [1x1] Regularization constant (default []); 
+%    If C = 0 (or C=1, default), it is hard margin, that is, 
+%       the model do not allow bounded support vectors
+%   .method [string] SVC cluster labeling Method
+%       'CG': Complete Graph Labeling Method. See Ref. 1 (default)
+%       'DD': Delaunay Diagram Labeling Method. See Ref. 4
+%       'MST': Minimum Spanning Tree Labeling Method. See Ref. 4
+%       'KNN': K-Nearest Neighbor Labeling Method. See Ref. 4
+%               >> options.k (number of K, default=4)
+%       'SEP-CG': SEP-based CG Labeling Method. See Ref. 2
+%       'E-SVC': Equilibrium vector based Labeling Method. See Ref. 3
+%          >> options.NofK (number of clusters, default = 0 (automatic determination) ) 
+%          --> We can control the number of clusters of SVC directly!
+%
+% Output:
+%  model [struct] from svdd.m
+%      .confusion_matrix:  (row) predicted cluster, (column) true cluster
+%      .cluster_labels [1 x num_data] predicted cluster labels
+%                --> ** NOTE: BSVs are classified as outliers (indexed by 0)
+%
+% Example
+%   load ring.mat;
+%   data.X=input';   % data.X: p x N input patterns
+%   options=struct('method','CG','ker','rbf','arg',0.5,'C',0.1);
+%   [model]=svc(data,options); 
+%   plotsvc(data,model);
+%
+%
+%
+% References  
+% 1. A.Ben-Hur,D.Horn,H.T.Siegelmann and V.Vapnik. Support Vector Clustring.
[…]

### 2016-03-22 talks/CausalBN/cbn2012.tex
x

--- 2016-03-22 talks/cbn-ppt-internal/cbn.tex
@@
 \usepackage{textpos} % package for the positioning
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{mathtools}
 \usetheme{Ilmenau} % change theme
-
+%% NEW COMMANDS
+\def\ci{\perp\!\!\!\perp}
+\def\dep{\perp\!\!\!\perp\!\!\!\!\!\!\!/\,\,\,\,}
 \begin{document}
@@
 %% MAKE TITLE
-\title{Basic Beamer Template}
-\subtitle{A subtitle should be placed here}
+\title{Learning Causation from Data}
+\subtitle{Fundamental of Casual Inference and its Applications}
 \author{Huang Xiao} %\\ \small{xiaohu@in.tum.de} }%\thanks{Funded by ARAMiS project}}
@@
 %% START PRESENTATION
-\section{Introduction}
-
-\begin{frame}{Introduction}
-
-\begin{itemize}
-\item Define the problem being studied.
-\item Explain your interest in the problem.
-\item Outline how the problem is to be investigated.
-\end{itemize}
-
-\end{frame}
-\subsection{XXX1}
-\begin{frame}{xxx1}
-
-\begin{itemize}
-\item Define the problem being studied.
-\item Explain your interest in the problem.
-\item Outline how the problem is to be investigated.
-\end{itemize}
-
-\end{frame}
-\subsection{XXX2}
-\begin{frame}{xxx2}
-
-\begin{itemize}
-\item Define the problem being studied.
-\item Explain your interest in the problem.
-\item Outline how the problem is to be investigated.
-\end{itemize}
-
-\end{frame}
-
-\section{History}
-
-\begin{frame}{History}
-
-\begin{itemize}
-\item Discuss the history of the problem.
-\item Describe context for the problem.
-\item Outline prior work on the problem.
-\end{itemize}
-
-\end{frame}
-
-\section{Representation}
-
-\begin{frame}{Representation}
-
-Represent the problem in symbolic, graphic, or numeric format.
-
-\bigskip
-
-Mathematical formulas may be typeset:
-\[ \int_0^\frac{\pi}{2}\frac{1+\cos 2x}{2} \: dx \]
-
-\end{frame}
-
-\section{Methods}
-
-\begin{frame}{Methods and Tools}
-
-Discuss technical methods or tools required to formulate and solve the problem mathematically.
-
-\bigskip
-
-\begin{theorem}
-If $f$ is continuous on $[a,b],$ then
-$$\int_{a}^{b} f(x) \: dx = F(b) - F(a)$$
-where $F$ is any antiderivative of $f,$ that is, a function such that $F' = f.$
-\end{theorem}
-
-\end{frame}
-
-\section{Solution}
-
-\begin{frame}{Solution of the Problem}
-
-Present a solution of the problem, perhaps for a simple case, and indicate how the solution may be achieved in other cases.
-
-\bigskip
-
-\begin{example}
-\[ \int_0^\frac{\pi}{2}\frac{1+\cos 2x}{2} \: dx=\frac{\pi}{4}  \]
-\end{example}
-
-\end{frame}
+\input{sections/fundamental}
+\input{sections/causalBN}
+\input{sections/copulaLearn}
+\input{sections/experiments}
 
 \section{Conclusion}
-
-\begin{frame}{Conclusion}
-
-Summarize the information presented in the talk.
-
-\bigskip
-
+\begin{frame}{Wrap up}
 \begin{itemize}
-\item Problem statement
-\item Relevance
-\item Mathematical tools
-\item Solution
+\item Causal Inference is a powerful tool for reasoning and predicting
+\item Graphical model has a strong representation on causal conditions
+\item Learning causation from data observation is totally feasible
+\item Without additional information, only equivalence class can be achieved
+\item Copula functions enable efficient parameter estimation
+\item PICM based structure learning is also efficient
+\item Promising experimental results show the interestingness of causal inference
 \end{itemize}
-
 \end{frame}
@@
 \section{References}
-
 \begin{frame}{References}
-
 \begin{thebibliography}{99}
-\bibitem{Boas} R. P. Boas,  Can we make mathematics intelligible?  \textit{Amer. Math. Monthly}, \textbf{88} (1981), 727--731.
-
-\bibitem{Page} M. E. Page,  A Brief Citation Guide for Internet Sources in History and the Humanities (Version 2.1),
-\begin{url}http://h-net.msu.edu/$\sim$africa/citation.html\end{url}.
-
+\bibitem{Boas} J. Pearls,  Causality: Models, Reasoning, and Inference  \textit{Cambridge University Press}, \textbf{2000}.
+\bibitem{Page} Joe Whittaker., Graphical Models in Applied Multivariate Statistics, \textit{John Wiley \& Sons}, Ltd, \textbf{2008}.
+\bibitem{Page} Roger B. Nelsen, An Introduction to Copulas, \textit{Springer Science+Business Media}, Inc, \textbf{2006}.
+\bibitem{Page} Jonas Peters, et al., Identifying Cause and Effect on Discrete Data using Additive Noise Models, \textit{JMLR}, Proceedings Track 9: 597-604, \textbf{2010}.
 \end{thebibliography}
-
 \end{frame}
-
 \end{document}

### 2016-04-13 h3lib.learn.api/H3GPR.py
push new files

@@ -1,0 +1,83 @@
+__author__ = 'morgan'
+import numpy as np
+from H3Kernels import kernel as kernel
+
+class H3GPR(object):
+    '''
+    Gaussian process regression main class
+    '''
+
+    def __init__(self, sigma=0.5, kernel='rbf', gamma=0.5,
+                 coef0=1, degree=2):
+        '''
+        object constructor
+        :param
+            sigma: noise level
+            kernel: string type of kernel, 'rbf','linear','polynomial'
+            gamma:
+        :return:
+        '''
+        self.sigma = sigma
+        self.kernel = kernel
+        self.gamma = gamma
+        self.coef0 = coef0
+        self.degree = degree
+
+    def fit(self, X, y, Xt):
+        '''
+        fit function of Gaussian process regression
+        :param X: observations
+        :param y: observation targets
+        :param Xt: test samples
+        :return: nx1 test targets
+        '''
+        n, d = X.shape
+        nt = Xt.shape[0]
+        K = kernel(X, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
+                   filter_params=True) + 1e-3
+        K_xt = kernel(X, Xt, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
+                   filter_params=True)
+        K_tt = kernel(Xt, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
+                   filter_params=True)
+        L = np.linalg.cholesky(K + self.sigma*np.eye(n))
+        K_inv = np.linalg.inv(K + self.sigma*np.eye(n))
+        alpha = K_inv.dot(y.reshape(n,1))
+        m = K_xt.T.dot(alpha).ravel()
+        S = K_tt - K_xt.T.dot(K_inv).dot(K_xt)
+        log_likelihood = -.5*y.reshape(1,n).dot(alpha) - np.log(L.diagonal()).sum() - .5*n*np.log(2*np.pi)
+        return m,S,log_likelihood
+
+
+if __name__ == '__main__':
+    import matplotlib.pyplot as plt
+    import utils.plot_utils as pltool
+
+    def obj_f(x):
+        # 1d function
[…]

### 2016-04-13 h3lib.learn.api/H3iSVC.py

@@ -1,0 +1,431 @@
+# from sklearn.metrics.pairwise import pairwise_kernels as kernel
+from H3Kernels import kernel
+import numpy as np
+
+
+class H3iSVC(object):
+    """
+    Class indicative SVC (Support vector clustering) using Ben-Hur's hypersphere solution
+    given partially labelled y.
+    """
+
+    def __init__(self, kernel='rbf', similarity=0.9,
+                 C=1.0, gamma=0.5, coef0=1, degree=3, eps=1e-4,
+                 labeling=False, display=False):
+        self.eps = eps                          # numerical tolerance level
+        self.kernel = kernel                    # kernel string, default is rbf, only 'rbf', 'linear', 'poly' are supported
+        self.alpha = None                       # dual variables
+        self.sv_ind = None                      # indices of SVs
+        self.bsv_ind = None                     # indices of BSVs
+        self.a2 = None                          # squared norm of center a
+        self.sv = None                          # store SVs + BSVs
+        self.sv_inx = None                      # indices of SVs+BSVs
+        self.nsv = None                         # number of SVs+BSVs
+        self.r = None                           # radius of the hypersphere
+        self.C = C                              # regularizer coef, default 1, no outlier is allowed
+        self.c_weighted = C                     # regularizer coef reweighted by indicative labels
+        self.k_diagonal = None                  # cache of diagonal kernel entries
+        self.impact_abnormal_indices = []       # indices of potentially abnormal points
+        self.impact_normal_indices = []         # indices of potentially normal points
+        self.similarity = similarity            # threshold to control the impact of given labels
+        self.gamma = gamma                      # param for rbf/poly kernel, default 1
+        self.coef0 = coef0                      # param for polynomial kernel, default 1
+        self.degree = degree                    # param for polynomial kernel, default 3
+        self.cluster_labels = None              # cluster labels
+        self.y = None                           # class labels, +1 abnormal, -1 normal
+        self.labeling = labeling                # call labeling process, default False
+        self.display = display                  # show details of solver
+
[…]

### 2016-04-13 h3lib.learn.api/__init__.py

@@ -1,0 +1,1 @@
+__author__ = 'morgan'

### 2016-04-13 h3lib.learn.api/H3GPR.py
add utils

@@ -41,11 +41,11 @@ class H3GPR(object):
                    filter_params=True)
         L = np.linalg.cholesky(K + self.sigma*np.eye(n))
         K_inv = np.linalg.inv(K + self.sigma*np.eye(n))
-        alpha = K_inv.dot(y.reshape(n,1))
+        alpha = K_inv.dot(y.reshape(n, 1))
         m = K_xt.T.dot(alpha).ravel()
         S = K_tt - K_xt.T.dot(K_inv).dot(K_xt)
-        log_likelihood = -.5*y.reshape(1,n).dot(alpha) - np.log(L.diagonal()).sum() - .5*n*np.log(2*np.pi)
-        return m,S,log_likelihood
+        log_likelihood = -.5*y.reshape(1, n).dot(alpha) - np.log(L.diagonal()).sum() - .5*n*np.log(2*np.pi)
+        return m, S, log_likelihood
 
 
 if __name__ == '__main__':
@@ -56,7 +56,7 @@ if __name__ == '__main__':
         # 1d function
         return np.array([np.sin(x0)+x0*np.cos(x0)-.1*x0**2 for x0 in x])
 
-    X = np.linspace(-5,5,100).reshape(100,1)
+    X = np.linspace(-5, 5, 100).reshape(100, 1)
     y = obj_f(X)
     given_idx = np.random.choice(y.size, 10)
     Xtr = X[given_idx]
@@ -74,10 +74,7 @@ if __name__ == '__main__':
         plt.plot(X[given_idx], y[given_idx], 'b+', ms=10, mfc='none', mec='b', mew=1)
         plt.fill_between(X.ravel(), m - 2*S.diagonal(), m + 2*S.diagonal(),
                          facecolor='blue', alpha=.1, edgecolor='none')
-        plt.gca().set(xlim=[-5,5])
+        plt.gca().set(xlim=[-5, 5])
         plt.gca().set(title='gamma='+str(g))
         plt.legend()
     plt.show()
-
-
-

### 2016-04-13 h3lib.learn.api/utils/dataset_viewer.py

@@ -1,0 +1,151 @@
+__author__ = 'morgan'
+import matplotlib.pyplot as plt
+import numpy as np
+from sklearn.decomposition import PCA, KernelPCA
+from sklearn.manifold import MDS
+import getopt,sys,os.path
+import utils.plot_utils as pltool
+
+class DatasetViewer(object):
+    '''
+    A class for dataset viewer used to analyse features in data
+    set straightforwardly
+    '''
+    def __init__(self):
+        pass
+
+    def view_features_distribution(self, X):
+        n,d = X.shape
+        indices = []
+        for i in np.arange(d):
+            indices.extend((i+1)*np.ones(n))
+        plt.gca().scatter(np.asarray(indices), X.T.flatten(),
+                          s=5, marker='.', alpha=0.5,facecolor='None',edgecolor='k')
+        plt.gca().plot([1,d],[0,0],'k-')
+        plt.gca().set(xlabel='feature id',
+                      ylabel='feature value',
+                      title='Feature distribution',
+                      xlim=[0,d-1])
+
+    def project2d(self, X, y=None, method='pca', g=0.5):
+        '''
+        Project high-dimensiona data to 2D for visulaization
+        using methods e.g., pca, kernel-pca, mds
+        :param X: N*d dataset
+        :param y: labels/None if not given
+        :param method: string in ['pca','kpca','mds']
+        :return: projected dataset X_project
+        '''
+        if y is not None and y.size != X.shape[0]:
+            exit("Data dims are not matched!")
+        else:
+            n_comp = 2
+            if method == 'pca':
+                projector = PCA(n_components=n_comp)
+                X_proj = projector.fit_transform(X)
+            elif method == 'kpca':
+                projector = KernelPCA(n_components=n_comp,kernel='rbf',gamma=g)
+                X_proj = projector.fit_transform(X)
+            elif method == 'mds':
+                projector = MDS(n_components=n_comp)
+                X_proj = projector.fit_transform(X)
+            else:
+                print 'No projector found!'
+                X_proj = X
+
+        if y is not None:
+            plt.gca().scatter(X_proj[:,0], X_proj[:,1], c=y, alpha=0.4)
+        else:
+            plt.gca().scatter(X_proj[:,0], X_proj[:,1])
+        plt.gca().set(xlabel='1st PC.',
+                      ylabel='2nd PC.',
+                      title=method)
+
+    def plot_corr(self, X, names=None):
+        n,d = X.shape
+        xcorr = np.corrcoef(X.T)
[…]

### 2016-04-13 h3lib.learn.api/utils/plot_utils.py

@@ -1,0 +1,34 @@
+__author__ = 'morgan'
+
+import numpy as np
+
+def getBoxbyX(X, grid=50, padding=True):
+    '''
+    Get the meshgrid X,Y given data set X
+    :param X: dataset
+    :param grid: meshgrid step size
+    :param padding: if add extra padding around
+    :return: X,Y
+    '''
+    if X.shape[1] > 2:
+        print 'We can only get the grid in 2-d dimension!'
+        return None
+    else:
+        minx = min(X[:,0])
+        maxx = max(X[:,0])
+        miny = min(X[:,1])
+        maxy = max(X[:,1])
+        padding_x = 0.05*(maxx-minx)
+        padding_y = 0.05*(maxy-miny)
+        if padding:
+            X,Y = np.meshgrid(np.linspace(minx-padding_x, maxx+padding_x, grid),
+                              np.linspace(miny-padding_y, maxy+padding_y, grid))
+        else:
+            X,Y = np.meshgrid(np.linspace(minx, maxx, grid),
+                              np.linspace(miny, maxy, grid))
+    return (X, Y)
+
+def setAxSquare(ax):
+    xlim0, xlim1 = ax.get_xlim()
+    ylim0, ylim1 = ax.get_ylim()
+    ax.set_aspect((xlim1-xlim0)/(ylim1-ylim0))

### 2016-04-13 h3lib.learn.api/H3iSVC.py
reshape code to flake8

@@ -51,9 +51,9 @@ class H3iSVC(object):
 
         # we use rbf kernel matrix for similarity measure
         # similarity from 0 to 1, if two points are identical, they are set as 1 else 0
-        K_abnormal = kernel(X[anomaly_idx], X, metric='rbf',  filter_params=True, gamma=self.gamma,
+        K_abnormal = kernel(X[anomaly_idx], X, metric='rbf', filter_params=True, gamma=self.gamma,
                                 coef0=self.coef0, degree=self.degree)
-        K_normal = kernel(X[normal_idx], X, metric='rbf',  filter_params=True, gamma=self.gamma,
+        K_normal = kernel(X[normal_idx], X, metric='rbf', filter_params=True, gamma=self.gamma,
                                 coef0=self.coef0, degree=self.degree)
         # filter out far points
         K_abnormal[K_abnormal < h] = 0
@@ -62,6 +62,7 @@ class H3iSVC(object):
         impact_normal_indices = np.where(K_normal >= h)
         K_impact = np.r_[K_abnormal, -K_normal]
         # positive impact score means the sample is more likely to be outlier
+
         def compute_f(K, id):
             nonzeros = K[:, id].nonzero()[0].size
             if nonzeros == 0:
@@ -152,7 +153,7 @@ class H3iSVC(object):
 
             # compute kernel submatrix K_BN which is the only requirement to update solution
             # TODO: replace with own kernel function
-            K_BN = kernel(X[(i1,i2),:], X, metric=self.kernel,  filter_params=True, gamma=self.gamma,
+            K_BN = kernel(X[(i1, i2), :], X, metric=self.kernel, filter_params=True, gamma=self.gamma,
                          coef0=self.coef0, degree=self.degree)
             k11 = K_BN[0, i1]
             k22 = K_BN[1, i2]
@@ -160,10 +161,10 @@ class H3iSVC(object):
 
             # compute 2nd derivative
             eta = k11+k22-2*k12
-            dist1 = (k11 - 2*np.dot(a[self.sv_inx].reshape(1,self.nsv),
-                                   K_BN[0, self.sv_inx].reshape(self.nsv,1)) + self.a2)[0,0]
-            dist2 = (k22 - 2*np.dot(a[self.sv_inx].reshape(1,self.nsv),
[…]

### 2016-04-13 h3lib.learn.api/H3iSVC.py
add some TODOs

@@ -141,18 +141,13 @@ class H3iSVC(object):
                     print 'identical samples found!'
                 return 0
             alph1, alph2 = a[i1], a[i2]
-            delta = alph1+alph2
+            delta = alph1 + alph2
             # determine lower/upper bound for alpha_2
-            L = np.array([0, delta-self.C]).max()
+            # TODO: what if L==H
+            L = np.array([0, delta - self.C]).max()
             H = np.array([self.C, delta]).min()
-            # if L/H are identical, exit update
-            # if np.abs(L-H) < 2*self.eps:
-            #     if self.display:
-            #         print 'identical bounds found!'
-            #     return 0
 
             # compute kernel submatrix K_BN which is the only requirement to update solution
-            # TODO: replace with own kernel function
             K_BN = kernel(X[(i1, i2), :], X, metric=self.kernel, filter_params=True, gamma=self.gamma,
                          coef0=self.coef0, degree=self.degree)
             k11 = K_BN[0, i1]
@@ -160,7 +155,7 @@ class H3iSVC(object):
             k12 = K_BN[0, i2]
 
             # compute 2nd derivative
-            eta = k11+k22-2*k12
+            eta = k11 + k22 - 2*k12
             dist1 = (k11 - 2*np.dot(a[self.sv_inx].reshape(1, self.nsv),
                                    K_BN[0, self.sv_inx].reshape(self.nsv, 1)) + self.a2)[0, 0]
             dist2 = (k22 - 2*np.dot(a[self.sv_inx].reshape(1, self.nsv),
@@ -175,9 +170,7 @@ class H3iSVC(object):
                     alph2_new = H
             else:
                 # 2nd derivative negative means minimum is on the bounds
-                # see my working notes
-                v1_v2 = (0.5-alph1)*k11 - (0.5-alph2)*k22 - (alph2-alph1)*k12 -\
-                            0.5*(dist1-dist2)
+                v1_v2 = (0.5-alph1)*k11 - (0.5-alph2)*k22 - (alph2-alph1)*k12 - 0.5*(dist1-dist2)
                 if L == 0:
                     delta_obj = (delta**2 - delta)*(k11-k22) + 2*delta*v1_v2
                 else:
@@ -201,7 +194,6 @@ class H3iSVC(object):
             setup_model(a)
 
             # update a2, r, fprime
-            # see my working notes
[…]

### 2016-04-16 h3lib.learn.api/H3GPR.py
refine gpr code

@@ -2,9 +2,11 @@ __author__ = 'morgan'
 import numpy as np
 from H3Kernels import kernel as kernel
 
+
 class H3GPR(object):
     '''
     Gaussian process regression main class
+    The implementation is referred to Rasmussen & Williams' GP book.
     '''
 
     def __init__(self, sigma=0.5, kernel='rbf', gamma=0.5,
@@ -13,8 +15,10 @@ class H3GPR(object):
         object constructor
         :param
             sigma: noise level
-            kernel: string type of kernel, 'rbf','linear','polynomial'
-            gamma:
+            kernel: string type of kernel, {'rbf','linear','polynomial'}
+            gamma: e.g., in rbf kernel: exp(-gamma|xj-xi|^2)
+            coef0: for linear kernel, e.g., coef0*XX^T
+            degree: for polynomial, e.g., |xi-xj|^(degree)
         :return:
         '''
         self.sigma = sigma
@@ -29,22 +33,23 @@ class H3GPR(object):
         :param X: observations
         :param y: observation targets
         :param Xt: test samples
-        :return: nx1 test targets
+        :return: predictive mean, covariance on test samples, and marginal log-likelihood on training set
         '''
         n, d = X.shape
-        nt = Xt.shape[0]
         K = kernel(X, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
                    filter_params=True) + 1e-3
         K_xt = kernel(X, Xt, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
-                   filter_params=True)
+                      filter_params=True)
         K_tt = kernel(Xt, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
-                   filter_params=True)
-        L = np.linalg.cholesky(K + self.sigma*np.eye(n))
-        K_inv = np.linalg.inv(K + self.sigma*np.eye(n))
+                      filter_params=True)
+        L = np.linalg.cholesky(K + self.sigma * np.eye(n))
+        K_inv = np.linalg.inv(K + self.sigma * np.eye(n))
         alpha = K_inv.dot(y.reshape(n, 1))
         m = K_xt.T.dot(alpha).ravel()
[…]

### 2016-04-16 h3lib.learn.api/H3Kernels.py

@@ -4,6 +4,7 @@ Kernel functions support RBF,linear,polynomial kernels
 '''
 import numpy as np
 
+
 def kernel(x1, x2=np.array([]), metric='linear', filter_params=True, coef0=1.0, degree=2, gamma=0.5):
     '''
     kernel methods support rbf, linear and polynomial
@@ -21,29 +22,28 @@ def kernel(x1, x2=np.array([]), metric='linear', filter_params=True, coef0=1.0, 
         x2 = x2.reshape(1, x2.size)
     if x2.size > 0 and x2.shape[1] != x1.shape[1]:
         exit("dims are not matched. exit!")
-    if metric not in ['linear','rbf','polynomial']:
+    if metric not in ['linear', 'rbf', 'polynomial']:
         exit('kernel type is not supported!')
 
     if metric == 'linear':
         if x2.size == 0:
-            return coef0*np.dot(x1, x1.T)
+            return coef0 * np.dot(x1, x1.T)
         else:
-            return coef0*np.dot(x1, x2.T)
+            return coef0 * np.dot(x1, x2.T)
 
     if metric == 'rbf':
         # TODO: this is still very slow
         if x2.size == 0:
-            n,d = x1.shape
+            n, d = x1.shape
             x1_norm = np.einsum('ij,ij->i', x1, x1)
-            eu_dists = x1_norm.reshape(n,1) - 2*np.dot(x1,x1.T) + x1_norm.reshape(1,n)
+            eu_dists = x1_norm.reshape(n, 1) - 2 * \
+                np.dot(x1, x1.T) + x1_norm.reshape(1, n)
         else:
-            n1,d1 = x1.shape
-            n2,d2 = x2.shape
+            n1, d1 = x1.shape
+            n2, d2 = x2.shape
             x1_norm = np.einsum('ij,ij->i', x1, x1)
             x2_norm = np.einsum('ij,ij->i', x2, x2)
-            eu_dists = x1_norm.reshape(n1,1) - 2*np.dot(x1,x2.T) + x2_norm.reshape(1,n2)
-        return np.exp(-gamma*eu_dists)
-
-
-
-
+            eu_dists = x1_norm.reshape(
+                n1, 1) - 2 * np.dot(x1, x2.T) + x2_norm.reshape(1, n2)
+        return np.exp(-gamma * eu_dists)
+    # TODO: implement polynomial kernel

### 2016-04-16 h3lib.learn.api/H3GPC.py
add GP classification implementation

@@ -1,0 +1,93 @@
+__author__ = 'morgan'
+import numpy as np
+from H3Kernels import kernel
+
+
+class H3GPC(object):
+    '''
+    Gaussian process classification main class
+    The implementation is referred to Rasmussen & Williams' GP book.
+    Note: we use Laplace appriximation and logistic function for GPC.
+    '''
+
+    def __init__(self, sigma=0.5, kernel='rbf', gamma=0.5,
+                 coef0=1, degree=2):
+        '''
+        object constructor
+        :param
+            sigma: noise level
+            kernel: string type of kernel, {'rbf','linear','polynomial'}
+            gamma: e.g., in rbf kernel: exp(-gamma|xj-xi|^2)
+            coef0: for linear kernel, e.g., coef0*XX^T
+            degree: for polynomial, e.g., |xi-xj|^(degree)
+        :return:
+        '''
+        self.sigma = sigma
+        self.kernel = kernel
+        self.gamma = gamma
+        self.coef0 = coef0
+        self.degree = degree
+        self.likelihood_f = lambda x: 1. / (1 + np.exp(-x))
+
+    def fit(self, X, y, Xt):
+        '''
+        fit function of Gaussian process regression
+        :param X: observations
+        :param y: binary labels
+        :param Xt: test samples
+        :return: predictive class probability for Xt (for y=+1)
+        '''
+        def laplace_mode(K, y):
+            # find the mode of the Laplace appriximation
+            f_new = f_old = np.zeros(n)
+            while np.linalg.norm(f_new - f_old) > 1e-4:
+                class_prob = self.likelihood_f(f_old)       # class=1 probability
+                log_prime = .5 * (y + 1) - class_prob.ravel()
+                W = np.diag(-class_prob * (1 - class_prob))
+                W_root = np.sqrt(W)
+                B = np.eye(n) + W_root.dot(K).dot(W_root)
+                B_inv = np.linalg.inv(B)
+                f_new = (K - K.dot(W_root).dot(B_inv).dot(W_root).dot(K)
+                         ).dot(W.dot(f_old.reshape(n, 1)) + log_prime)
+
[…]

### 2016-04-16 h3lib.learn.api/H3GPC.py
mean, variance of predictive distribution of given test samples are computed.

@@ -4,15 +4,15 @@ from H3Kernels import kernel
 
 
 class H3GPC(object):
-    '''
+    """
     Gaussian process classification main class
     The implementation is referred to Rasmussen & Williams' GP book.
     Note: we use Laplace appriximation and logistic function for GPC.
-    '''
+    """
 
     def __init__(self, sigma=0.5, kernel='rbf', gamma=0.5,
                  coef0=1, degree=2):
-        '''
+        """
         object constructor
         :param
             sigma: noise level
@@ -21,7 +21,7 @@ class H3GPC(object):
             coef0: for linear kernel, e.g., coef0*XX^T
             degree: for polynomial, e.g., |xi-xj|^(degree)
         :return:
-        '''
+        """
         self.sigma = sigma
         self.kernel = kernel
         self.gamma = gamma
@@ -30,20 +30,21 @@ class H3GPC(object):
         self.likelihood_f = lambda x: 1. / (1 + np.exp(-x))
 
     def fit(self, X, y, Xt):
-        '''
+        """
         fit function of Gaussian process regression
         :param X: observations
         :param y: binary labels
         :param Xt: test samples
         :return: predictive class probability for Xt (for y=+1)
-        '''
+        """
+
         def laplace_mode(K, y):
             # find the mode of the Laplace appriximation
             f_new = f_old = np.zeros(n)
             while np.linalg.norm(f_new - f_old) > 1e-4:
                 class_prob = self.likelihood_f(f_old)       # class=1 probability
                 log_prime = .5 * (y + 1) - class_prob.ravel()
-                W = np.diag(-class_prob * (1 - class_prob))
+                W = np.diag((class_prob * (1 - class_prob)).ravel())
                 W_root = np.sqrt(W)
                 B = np.eye(n) + W_root.dot(K).dot(W_root)
                 B_inv = np.linalg.inv(B)
@@ -55,18 +56,19 @@ class H3GPC(object):
         n, d = X.shape
         K = kernel(X, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
                    filter_params=True) + 1e-3
-        K_xt = kernel(Xt, X, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
+        K_xt = kernel(X, Xt, metric=self.kernel, gamma=self.gamma, coef0=self.coef0, degree=self.degree,
[…]

### 2016-08-09 ml_notes/draft.tex
edit draft.tex
add GPC subsection
- recent working notes for ML - stanford webpage

@@
 \documentclass{article}
+\usepackage{nips15submit_e,times}
 
-% use Times
-\usepackage{times}
 % For figures
@@
 
-% Employ the following version of the ``usepackage'' statement for
-% submitting the draft version of the paper for review.  This will set
-% the note in the first column to ``Under review.  Do not distribute.''
-\usepackage[accepted]{icml2016}
-
-% Employ this version of the ``usepackage'' statement after the paper has
-% been accepted, when creating the final version.  This will set the
-% note in the first column to ``Proceedings of the...''
-%\usepackage[accepted]{icml2016}
 %-------------------------------------------------------------
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \newcommand{\cbn}{\textsc{Cbn}}
@@
 \newcommand{\con}[1]{\ensuremath{\mathsf{#1}}}
+\newcommand{\bb}[1]{\ensuremath{\mathbb{#1}}}
 \newcommand{\T}{\ensuremath{\top}}
@@
 \newcommand{\bmat}[1]{\begin{bmatrix}#1\end{bmatrix}}
-\newcommand{\mname}{\texttt{OLCS}}
 \newcommand{\question}[1]{\textcolor{red}{Q: #1}}
-\newcommand{\lrb}{\left{\right}}
 
-% The \icmltitle you define below is probably too long as a header.
-% Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Machine learning working notes}
+\title{Machine Learning Working Notes}
+
+\author{
+	Huang Xiao\thanks{Visiting homepage: feuerchop.github.io} \\
+	Department of Computer Science\\
+	Technical University of Munich\\
+	Munich, Germany 85748 \\
+%	\texttt{hippo@cs.cranberry-lemon.edu} \\
+%	\And
+%	Coauthor \\
+%	Affiliation \\
+%	Address \\
+%	\texttt{email} \\
+%	\AND
+%	Coauthor \\
+%	Affiliation \\
+%	Address \\
+%	\texttt{email} \\
+%	\And
+%	Coauthor \\
+%	Affiliation \\
+%	Address \\
+%	\texttt{email} \\
+%	\And
+%	Coauthor \\
+%	Affiliation \\
+%	Address \\
+%	\texttt{email} \\
+%	(if needed)\\
+}
+
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to \LaTeX{} to determine where to break
+% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
+% puts 3 of 4 authors names on the first line, and the last on the second
+% line, try using \AND instead of \And before the third author name.
+
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+
+\nipsfinalcopy % Uncomment for camera-ready version
 
 \begin{document}
-
-\twocolumn[
-\icmltitle{Machine Learning Working Notes}
-
-% It is OKAY to include author information, even for blind
-% submissions: the style file will automatically remove it for you
-% unless you've provided the [accepted] option to the icml2016
-% package.
-\icmlauthor{Huang Xiao}{xiaohu@in.tum.de}
-\icmladdress{Technische Universit\"{a}t M\"{u}nchen,
-	Boltzmannstr.3, D-85743 Garching b. M\"{u}nchen, Germany}
-%\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
-%\icmladdress{Their Fantastic Institute,
-%            27182 Exp St., Toronto, ON M6H 2T1 CANADA}
-
-% You may provide any keywords that you
-% find helpful for describing your paper; these are used to populate
-% the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{Machine learning}
-
-\vskip 0.3in
-]
+\maketitle
 
@@
 \end{abstract}
+\section{Linear Models}
+\subsection{Regression}
+It seems everything starts to grow from linear model, whatever regression or classification, linear models expand to almost many other learning models we face during the research.
+So starting from a very simple linear regression problem, given training set $\set D = \left\{ \vct x_i, \vct y_i \right\}_{i=1}^n $ with $ n $ sample, where $ \vct y $ are the responses as numerical values.
+A linear regression model finds a linear weight vector, which minimizes a certain type of empirical error.
+This is obviously defined in perspective of statistical learning theory.
+\begin{equation}
+\argmin_{\vct w} \frac{1}{n}\sum_{i=1}^n \| w^T x_i + b - y_i\|^2
+\end{equation}
+where empirical error introduced by individual sample is equally weighted by $ 1/n $.
+It is seen that we are using a straight line to fit a possibly any shaped function, obviously the summation or mean error can be large due to the noise or intrinsic nonlinearity of function.
+However, a typical misunderstanding of linear model for beginners is that the term linear refers to $ \vct w $ instead of $ \vct x $.
+That is to say, we are expecting a linear model on parameters $ \vct w $, but the feature vectors $ \vct x $ can actually be any shape.
+Therefore, in literature we mostly see a feature mapping of input $ \vct x $ as $ \phi(\vct x) $, and it does not break the linear property of the model.
+Therefore, we have our liner model as,
+\begin{equation}
+\argmin_{\vct w} \frac{1}{n}\sum_{i=1}^n \| w^T \phi(x_i) + b - y_i\|^2
+\label{eq:linear_reg}
+\end{equation}
+A typical feature mapping is polynomial feature mapping. Suppose we have a 2-dimensional input data sample $ \left( x_1, x_2 \right) $, we define a feature mapping as follows,
+\[ \left( x_1, x_2 \right) \rightarrow \left( x_1, x_2, x_1^2+x_2^2 \right)\], where a 2-d plane is transformed as a paraboloid in 3-d space.
+Substituting back into previous linear function, it becomes a polynomial line fitting problem, but it is still linear in $ \vct w $.
 
-\section{Gaussian Process Regression}
+To solve the least square problem defined in Eq.
+\ref{eq:linear_reg} to obtain an optimal parameter estimation $ \vct w $, we take the gradient with respect to the loss and set it to zero.
+Note that the intercept $ b $ can be folded in vector $ \vct w $ by adding additional entry $1$ in the end, for simplicity, we ignore it in our formulation.
+The least square solution is,
+\begin{equation}
+\vct w^* = \left( \Phi(\vct X)^T\Phi(\vct X) \right)^{-1}\Phi(\vct X)^T\vct Y
+\label{eq:lsq_sol}
+\end{equation}
+As long as the $ \Phi(\vct X)^T\Phi(\vct X) $ is not singular, there exists analytical solution.
+We will call $ \Phi(\vct X) $ design matrix, which takes each row as a feature mapping on $ \vct x $.
+We will see in short that the inner product of feature mapping can be explicitly defined by a certain kernel function, which established a very important chapter of learning theory, \ie \textit{Kernel Methods}.
+To predict the response for a new sample $ \vct x^* $, we have,
+\[ \vct y^* = \phi(\vct x^*) \left( \Phi(\vct X)^T\Phi(\vct X) \right)^{-1}\Phi(\vct X)^T\vct Y \]
+
+\subsubsection*{From Probabilistic View}
+Different from minimizing empirical errors from observations, we can examine the whole problem in a probabilistic view, that is, minimize the uncertainty from observations.
+If we reformulate the problem as a summation of a deterministic function and a indeterministic noise from a certain probabilistic distribution, we can write the linear model as,
+\[ \vct y = \vct w^T \phi(\vct x) + \epsilon \], where $ \epsilon \sim \set N\left( 0, \sigma^2 \right)$ which is defined as a Gaussian noise, the bias term $ b $ is again folded in $ \vct w $.
+Moreover, we can get the response $ \vct Y $ as a Gaussian distribution as well.
+\[ \vct Y \sim \prod_{i=1}^n \set N\left( \vct w^T\phi(\vct x_i), \sigma^2 \right) \]
+In order to get the optimal parameter $ \vct w $, we need to maximize the likelihood $ p\left( \vct Y\mid \vct X, \vct w \right) $.
+It equals to maximize the log-likelihood, and the log-likelihood gives,
+\begin{equation}
+\ln p\left( \vct Y \mid \vct X, \vct w \right) = -\frac{n}{2}\ln(2\pi)-n\ln(\sigma) - \frac{1}{2\sigma^2}\|\vct Y - \Phi(\vct X)\vct w\|^2
+\label{eq:mle}
+\end{equation}
+From Eq.\ref{eq:mle}, we can see maximizing the log-likelihood (\textit{MLE}) equals minimizing the least squared error. We will get the exact same solution as in Eq.\ref{eq:lsq_sol}.
+
+\subsubsection*{Overfitting}
+Now suppose we have four 1-dimensional observations $ \vct X $, and define an arbitrary feature mapping $ \phi $, we expect to find a linear model to minimize the least squared error, as we see in \eqref{eq:linear_reg}.
+\[ \bmat{2 \\ 1 \\-1} = \phi\left( \bmat{1.5 \\ 0.5 \\ 2.5} \right)  \vct w \]
+If we define the feature mapping $ \phi $ as 
+\[  \bmat{1.5 \\ 0.5 \\ 2.5} \xrightarrow{\phi} \bmat{1 & 0 & 0 \\ 0 & 1 & 0\\ 0 & 0 & 1}\]
+We can see that $ \vct w $ is exactly the response vector $ \vct y $, and the least squared error is minimized as zero.
+A feature mapping can always be defined to achieve zero error, if there's no constraints at all.
+But obviously, there is no benefit to use this linear model on any prediction task, and mostly likely we will get a very high prediction error based on that.
+If the model performs well on training dataset, but poorly on unseen data, we can call this situation as overfitting.
+And certainly, overfitting is a central problem that machine learning attempts to solve.
+
+To avoid overfitting, we can firstly introduce constraint by adding a penalty term on the complexity of the $ \vct w $, which is known as \textit{regularization}.
+For example, by penalizing a 2-norm of $ \vct w $, we can generalize the least squared error problem as,
+\begin{equation}
+\argmin_{\vct w} \frac{1}{n}\sum_{i=1}^n \| \vct w^T \phi(x_i) + b - y_i\|^2 + \frac{\lambda}{2}\vct w^T\vct w 
+\label{l2norm}
+\end{equation}
+Similarly taking the derivative w.r.t. $ \vct w $ and set to zero, we can get the optimal parameters as,
+\begin{equation}
+\vct w^* = \left( \Phi(\vct X)^T\Phi(\vct X) + \lambda \vct I \right)^{-1}\Phi(\vct X)^T\vct Y
+\label{eq:lsq_reg_sol}
+\end{equation}
+Again from probabilistic view, we introduce uncertainty on $ \vct w $ instead of only considering uncertainty on response $ \vct y $.
+Define a prior on $ \vct w $ following a D-dimensional Gaussian distribution,
+\[ \vct w \sim \set N\left( \vct 0, \Sigma_{\vct w} \right) \] 
+We want to capture the posterior distribution on $ \vct w $ after observations of $ \left( \vct X, \vct Y \right) $, that is, the objective is to maximize the posterior according to Bayes theorem,
+\begin{equation}
+\max p\left( \vct w \mid \vct X, \vct Y \right) = \frac{p\left( \vct Y \mid \vct X, \vct w \right)p\left( \vct w \right)}{\int p\left( \vct Y \mid \vct X, \vct w \right)p\left( \vct w \right)d\vct w}
+\label{eq:posterior}
+\end{equation}
+The denominator in Eq.\ref{eq:posterior} is also called marginal likelihood, which is independent of $ \vct w $, therefore, taking the logarithm of the posterior, we have,
+\begin{equation}
+\ln p\left( \vct w \mid \vct X, \vct Y \right) = -\frac{(n+d)}{2}\ln(2\pi)-n\ln(\Sigma_{\vct w}) - \frac{1}{2}\ln|\Sigma_{\vct w}|- \frac{1}{\sigma^2}\|\vct Y - \Phi(\vct X)\vct w\|^2 - \frac{1}{2}\vct w^T\Sigma_{\vct w}^{-1}\vct w
+\label{eq:ln_posterior}
+\end{equation}
+Take the gradient w.r.t. $ \vct w $ and set to zero, we can get very similar results as in Eq.\ref{eq:lsq_reg_sol}.
+\begin{equation}
+\vct w_{map} = \left( \Phi(\vct X)^T\Phi(\vct X) + \sigma^2\vct \Sigma_{\vct w}^{-1} \right)^{-1}\Phi(\vct X)^T\vct Y
+\label{map_sol}
+\end{equation}
+If the prior is defined with an isotropic Gaussian, we see that the \textit{MAP} solution is equivalent to $ \ell_2 $ regularization form. Now let us look back at the posterior, note that,
+\begin{align}
+p\left( \vct w \mid \vct X, \vct Y \right) & \propto p\left( \vct Y \mid \vct X, \vct w \right)p\left( \vct w \right)  \nonumber\\
+& \propto \exp \left\lbrack -\frac{1}{2\sigma^2}\left( \Phi(\vct X)\vct w - \vct Y\right)^T\left( \Phi(\vct X)\vct w - \vct Y\right) \right\rbrack \exp \left( \frac{1}{2}\vct w^T\Sigma_{\vct w}^{-1}\vct w \right)  \nonumber\\
+& \propto \exp\left\{ -\frac{1}{2}\vct w^T\left( \frac{1}{\sigma^2}\Phi(\vct X)^T \Phi(\vct X) + \Sigma_{\vct w}^{-1}\right)\vct w + \frac{1}{\sigma^2}\vct Y^T\Phi(\vct X)\vct w \right\}
+\end{align}
+By completing the square we can get the mean and covariance of the posterior, that is, 
+\begin{align}
+ \vct w^* &\sim\set N \left( \vct m^*,  \vct A^{-1} \right) \nonumber \\
+ \vct m^* &= \frac{1}{\sigma^2} \vct A^{-1} \Phi(\vct X)^T\vct Y \\
+  \vct A  &= \frac{1}{\sigma^2}\Phi(\vct X)^T\Phi(\vct X)+\Sigma_{\vct w}^{-1}
+\end{align}
+And we see that the \textit{MAP} solution is exactly the same as the mode of the posterior.
+To predict a new input sample $ \vct x^* $, we can derive a predictive distribution instead of just a single value at the mode, and it is again a Gaussian with posterior mean multiplied with the test sample, and variance of the predictive distribution is the quadratic form on the posterior covariance, which grows with the magnitude of test samples.
+\begin{align} 
+	p(\vct y^* \mid \vct X, \vct Y, \vct x^*) & = \int p(\vct y^*\mid \vct X, \vct Y, \vct w, \vct x^*)p(\vct w \mid \vct X, \vct Y)d\vct w  \nonumber \\
+	& \sim \set N\left( \vct \Phi(\vct x^*)^T \vct m^*, \Phi(\vct x^*)^T \vct A^{-1} \Phi(\vct x^*) \right)
+\end{align}
+
+\subsection{Classification}
+Now let us consider classification problem, where we expect a functional $ \pi(\vct x) $ to map input to class labels, in binary case $ \vct y=\left\{ +1, -1 \right\} $.
+
+\section{Gaussian Process}
+\subsection{Regression}
 \label{sec:gpr}
@@
 \begin{align}
-	& \mu_* = K_{X_*,X}\left[K_{X,X}+\sigma_n^2 I\right]^{-1}\vct y \label{eq:gpr_mu}\\
-	& \Sigma_*^{-1} = K_{X_*,X_*} - K_{X_*,X}\left[K_{X,X}+\sigma_n^2 I\right]^{-1}K_{X,X_*} \label{eq:gpr_cov}
+	& \bar{f_*} = \vct k_{*}^T (\vct K +\sigma_n^2 I)^{-1}\vct y \label{eq:gpr_mu}\\
+	& \bb{V}(f_*) = k(\vct x_*, \vct x_*) - \vct k_{*}^T (\vct K+\sigma_n^2 I)^{-1} \vct k_{*}  \label{eq:gpr_cov}
 \end{align}
-where $\sigma_n^2$ is the noise level and $K_{\cdot,\cdot}$ represents a shorthand for covariance matrix.
-\question{Here comes the question of how to estimate the parameters for the covariance $K$.}
+where $\sigma_n^2$ is the noise level, $\vct K$ represents a shorthand for covariance matrix on input $ \vct X $, and we denote $ \vct k_{*} $ as the kernel function $ k(\vct X, \vct x_*) $ for simplicity.
+%\question{Here comes the question of how to estimate the parameters for the covariance $K$.}
 
@@
 \]
+
+Now looking at the predictive mean of training dataset, which can be given by Eq.\eqref{eq:gpr_mu}-\eqref{eq:gpr_cov} on training set $ \vct X $ itself, 
+\[ \bar{f} = \vct K(\vct K + \sigma_n^2 I)^{-1}\vct y \]
+
+Since $ \vct K $ is symmetric positive definite and its eigendecomposition is $ \vct K=\sum_{i=1}^n \lambda_i\vct u_i \vct u_i^T$, where $ \lambda_i $ is the \textit{i}th eigenvalue and $ \vct u_i $ is the \textit{i}th eigenvector.
+Now define a vector $ \vct U=\bmat{\vct u_1, \ldots, \vct u_n} $, therefore we have $ \vct K = \vct U\Sigma\vct U^T $.
+According the the matrix inverse lemma [\cite{mil86}], we can derive a simple form for the predictive mean, where we observe that the predictive mean is a linear smooth on their targets.
+
+\begin{align*}
+\bar{f} & = \vct K\left( \sigma_n^{-2}I - \sigma_n^{-2}I\vct U \left( \Sigma^{-1}+\vct U^T\sigma_n^{-2}I\vct U \right)^{-1}\vct U^T\sigma_n^{-2}I\right)\vct y \\
+& = \vct K\left( \sigma_n^{-2}I - \sigma_n^{-2}\vct U \left( \Sigma^{-1}+\sigma_n^{-2}I \right)^{-1}\vct U^T\sigma_n^{-2}\right)\vct y \\
+& = \left( \sigma_n^{-2}\vct U\Sigma\vct U^T - \vct U\Sigma
+			\bmat{\frac{\lambda_1\sigma_n^{-2}}{\lambda_1+\sigma_n^{2}} & & \\ 
+						& \ddots & \\ 
+						& & \frac{\lambda_n\sigma_n^{-2}}{\lambda_n+\sigma_n^{2}}}
+		\vct U^T \right)\vct y \\
+& = \left( \sigma_n^{-2}\vct U\Sigma\vct U^T - \sigma_n^{-2}\vct U
+\bmat{\frac{\lambda_1^2}{\lambda_1+\sigma_n^{2}} & & \\ 
+	& \ddots & \\ 
+	& & \frac{\lambda_n^2}{\lambda_n+\sigma_n^{2}}}
+\vct U^T \right)\vct y \\
+& = \left( \sigma_n^{-2}\sum_{i=1}^n\lambda_i\vct u_i\vct u_i^T - \sigma_n^{-2}\sum_{i=1}^n \frac{\lambda_i^{2}}{\lambda_i + \sigma_n^2}\vct u_i\vct u_i^T \right)\vct y \\
+& = \sum_{i=1}^n \frac{\lambda_i}{\lambda_i + \sigma_n^2}\vct u_i\vct u_i^T\vct y \\
+& = \sum_{i=1}^n \frac{\gamma_i\lambda_i}{\lambda_i + \sigma_n^2}\vct u_i, \quad \text{with } \gamma_i = \vct u_i^T\vct y
+\end{align*}
+
+\subsection{Classification}
+Using Gaussian process for classification task is a bit more complicated than regression.
+The main idea of it is to use a `squash' function to convert a predicted function value within $\left[ 0, 1\right]$, \eg, sigmoid function, cumulative Gaussian \textit{pdf}.
+Given a dataset $\set D = \left\{x_i\right\}_{i=1}^n$ with $x_i \in R^d$ and corresponding labels $\vct y=\left[ +1,-1 \right] $
+
+\section{Support Vector Machines}
 

### 2016-11-03 ml_notes/draft.tex
- change to new MBP

@@
 \subsection{Classification}
-Now let us consider classification problem, where we expect a functional $ \pi(\vct x) $ to map input to class labels, in binary case $ \vct y=\left\{ +1, -1 \right\} $.
+Now let us consider classification problem, where we expect a functional $ \pi(\vct x) $ to map input $ \vct x $ to class labels, in binary case $ \vct y=\left( +1, -1 \right) $.
+More commonly, we can define a Bernoulli distribution $ p(y=+1 \mid x) $ for one class and $ 1-p\left( y=+1 \mid x \right) $ for another.
+Typically, we would choose a sigmoid function, \eg logistic function or \textit{tanh} to warp a possibly infinite value into a bounding box, \eg, $ \left\lbrack 0, 1 \right\rbrack $ for logistic function.
+This is a desired behavior, since any function value will be transformed to a probability.
+A logistic function is defined,
+\[ \sigma(a) = \frac{1}{1+\exp(-a)} \]
+Obviously, we also have, 
+\begin{align*}
+\sigma(-a) = 1-\sigma(a) \\
+\tanh(a) = 2\sigma(2a) -1 \\
+\diff{\sigma(a)}{a} = \left( 1-\sigma(a) \right)\sigma(a)
+\end{align*}
+Thus, the conditional class distribution given input dataset can be defined as a sigmoid function on the linear model $ p\left( y \mid \vct x \right) = \sigma(yf(\vct x))$, again we fold the bias term $ b $ in the parameters $ \vct w $.
 

### 2016-11-03 h3lib.learn.api/MyClassifier.py

@@ -1,0 +1,117 @@
+"""
+Base class for machine learning classifier. It is an abstract class defining
+methods need to be implemented in subclasses.
+
+Author: Huang Xiao
+Email: xh0217@gmail.com
+Copyright@2016, Stanford
+"""
+
+from abc import ABCMeta, abstractmethod
+from datetime import datetime
+import dill
+import numpy as np
+
+class MyClassifier(object):
+
+    '''
+    Abstract class for classifiers of SmartEngine.
+    All smart components should inherit from this super class.
+    '''
+
+    __metaclass__ = ABCMeta
+
+    def __init__(self, name='MyClassifier', preprocessor=None, max_epoch=10, verbose=False):
+        '''
+        Initialization
+        :param name: the name of the classifier
+        :param preprocessor: a list of preprocessors
+        :param max_epoch: maximal epochs to train
+        :param verbose: verbose print out information
+        '''
+        self.name = name
+        self.max_epoch = max_epoch
+        self.status = 'untrained'
+        self.preprocessor = preprocessor
+        self.verbose = verbose
+
+    @abstractmethod
+    def train(self, featureset, labelset):
+        # # train on a training dataset
+        # if self.verbose:
+        #     print '\t\t[INFO][{:s}] classifier is trained on {:d} samples ...'.format(datetime.now().strftime('%Y-%m-%d %H:%M:%S'),
+        #                                                                       featureset.shape[0])
+        pass
+
+    @abstractmethod
+    def update(self, minibatch_featureset, minibatch_labelset):
+        # update model on a minibatch
+        # if self.verbose:
+        #     print '\t\t[INFO][{:s}] classifier is updated on {:d} samples ...'.format(datetime.now().strftime('%Y-%m-%d %H:%M:%S'),
+        #                                                                       minibatch_featureset.shape[0])
+        pass
+
+    @abstractmethod
+    def predict(self, test_featureset):
+        # predict outputs for test dataset
+        pass
+
+    def save(self, path):
+        # save checkpoint for the predictive model
+        dill.dump(self, open(path, 'w'))
+        if self.verbose:
+            print '\t[INFO][{:s}] classifier checkpoint is saved at {:s} ...'.format(datetime.now().strftime('%Y-%m-%d %H:%M:%S'),
+                                                                    path)
+
+    def add_preprocessor(self, pc):
+        '''
+        Append additional preprocessor to the list of preprocessor in this classifier.
[…]

### 2016-11-03 h3lib.learn.api/Preprocessor.py

@@ -1,0 +1,75 @@
+"""
+Preprocessor is a class used to preprocess the raw data to machine learning readable dataset.
+The run method in Preprocessor will iterate over each worker to process your input data, output
+is a N*D numeric trainable dataset, where N is the number of training samples, and D is the feature dimensionality.
+
+You need to define a proper preprocessor with a proper pipeline of workers for the classifier you are using.
+
+Author: Huang Xiao
+Email: xh0217@gmail.com
+Copyright@2016, Stanford
+"""
+
+class Preprocessor(object):
+    """
+    Preprocessor main class: the pipeline for preprocessing raw data to generate vectorized feature set
+    It is mainly used in the first step in any learning cycle.
+    """
+
+    def __init__(self, pipeline, feature_names=list()):
+        """
+        Preprocessing the raw data to build feature vectors, we use a pipeline to get our job done
+        :param data_raw: raw data as in QuickTemplate.train
+        :return: vectorized dataset for further process
+        """
+
+        # after initialization pipeline is a list of objects to prepare the feature vectors
+        import importlib
+
+        self._PIPELINE = list()
+        self._FEATURE_NAMES = feature_names
+        self._FEATURE_SIZE = 0
+        for elem in pipeline:
+            worker_class = getattr(importlib.import_module("SmartEngine.PipelineWorkers"), elem['worker'])
+            if elem.has_key('params'):
+                worker = worker_class(elem['params'])
+            else:
+                worker = worker_class()
+            self._PIPELINE.append(worker)
+
+
+    def run(self, data_raw, restart=False):
+        """
+        Start processing
+        :param data_raw:
+        :return: feature set for training
+        """
+
+        for worker in self._PIPELINE:
+            if restart or not worker.fitted:
+                data_raw = worker.transform(data_raw)
+            else:
+                data_raw = worker.partial_transform(data_raw)
+
+            # we set the feature names from HashParser's feature mapping
+            if worker.__class__.__name__ == 'HashParser':
+                self._FEATURE_NAMES = worker.feature_mapping.keys()
+        self._FEATURE_SIZE = data_raw.shape[1]
+        return data_raw
+
+
+if __name__ == '__main__':
+    import json
+
+    #data_raw = json.load(open('../feed.json'))
+    data_raw = json.load(open('../feed.json'))
[…]

### 2016-11-03 h3lib.learn.api/QuickTemplate.py

@@ -1,0 +1,224 @@
+"""
+QuickTemplate is the classifier class for tempalte suggestion in MyriadHub. It subclasses MyClassifier and is
+instantiated with a proper preprocessor. The classifier uses SGD logistic regression for multi-class classification.
+
+For more details on how to use SGD logistic regression and its corresponding parameters, please checkout:
+http://scikit-learn.org/stable/modules/sgd.html
+
+Author: Huang Xiao
+Email: xh0217@gmail.com
+Copyright@2016, Stanford
+"""
+
+from Preprocessor import *
+import numpy as np
+from sklearn.grid_search import GridSearchCV
+from sklearn.linear_model import SGDClassifier
+from datetime import datetime
+from MyClassifier import MyClassifier
+
+
+class QuickTemplate(MyClassifier):
+   """
+   QuickTempalte main class: a smart template recommendation system used to facilitate easy email reply.
+   We are using stochastic gradient descent logistic regression for prediction.
+   """
+
+   def __init__(self,
+                preprocessor=None,
+                loss='log',
+                penalty='l2',
+                alpha=0.0001,
+                shuffle=True,
+                class_weight=None,
+                max_epoch=10,
+                verbose=True):
+      """
+      Constructor
+      :return:
+      """
+
+      super(QuickTemplate, self).__init__('Template Suggesting Model', max_epoch=max_epoch, verbose=verbose)
+      # training params / optimal training params after model selection
+      self.loss = loss
+      self.penalty = penalty
+      self.alpha = alpha
+      self.shuffle = shuffle
+      if preprocessor is None:
+         # the default preprocessor is a Tfidf vectorizer
+         self.preprocessor = Preprocessor(pipeline=[('TfidfVectorizer', {'encoding': 'utf-8'})])
+      else:
+         self.preprocessor = preprocessor
+      # default classifier is SGD logistic regressor
+      self.clf = SGDClassifier(loss=self.loss,
+                               penalty=self.penalty,
+                               alpha=self.alpha,
+                               shuffle=self.shuffle,
+                               class_weight=class_weight)
+      # if verbose:
+      #     print '[INFO][{:s}] {:s} is initialized.'.format(datetime.now().strftime('%Y-%m-%d %H:%M:%S'),
+      #                                                  self.name)
+
[…]

### 2016-11-03 h3lib.learn.api/test.py

@@ -1,0 +1,79 @@
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.decomposition import PCA, KernelPCA
+from sklearn.naive_bayes import GaussianNB
+from sklearn.ensemble import RandomForestClassifier as RFClassifier
+from sklearn.linear_model import SGDClassifier
+from sklearn.manifold import MDS
+from sklearn.svm import SVC
+from utils import plot_utils
+from sklearn import cross_validation as cv
+from sklearn.grid_search import GridSearchCV
+from sklearn.datasets import load_digits
+import random
+
+# preconfigure dataset
+# ----- read MyriadHub data from JSON file
+#mydata = pickle.load(open('../feed_dataset.p', 'rb'))
+#Xtr = mydata['vectors'].todense()
+#ytr = np.array(mydata['labels'])
+## multiple labels
+#original_labels = ytr.copy()
+## binary labels
+#ytr[ytr!=0] = 1
+#ytr[ytr==0] = -1
+#print "here1"
+
+ #test digits dataset
+digits = load_digits()
+Xtr = digits.data
+original_labels = digits.target
+
+# initialize classifiers
+#clf_svm_part = SVC(kernel='rbf', C=20, gamma=20, class_weight='auto') #n_iter = 1
+#clf_svm = SVC(kernel='rbf', C=20, gamma=20, class_weight='auto')
+#clf_gaussnb = GaussianNB()
+#clf_randforest = RFClassifier(n_estimators=10)
+#clf_logreg = SGDClassifier(loss="log", warm_start=True, alpha=0.0001)
+print "here2"
+
+# model selection for all classifiers 
+#model_selector_svm_part =  ?
+#model_selector_svm = GridSearchCV(estimator=clf_svm, param_grid=dict(C=np.logspace(0.1,10,10),
+#                                                      gamma=np.logspace(0.1,10,10)),
+#                      verbose=1)
+#model_selector_gaussnb = GridSearchCV(estimator=clf_gaussnb, param_grid=dict(),
+#                      verbose=1)
+#model_selector_randforest = GridSearchCV(estimator=clf_randforest, param_grid=dict(n_estimators=range(2,21)),
+#                      verbose=1)
+#model_selector_logreg = GridSearchCV(estimator=clf_logreg, param_grid=dict(alpha=np.logspace(0.0001,50,10)),
+#                      verbose=1)
+print "here3"
+
[…]

### 2016-11-03 h3lib.learn.api/test/testDataBatchHelper.py

@@ -1,0 +1,11 @@
+from SmartEngine.utils.dataset_helper import *
+
+event_json = '../../fixed2-mlTestCampaignCuris1.json'
+
+print '#1: test get_data_batch... '
+res = get_data_batch(event_json)
+json.dump(res, open('temp.json', 'w'))
+print 'templates used: ', res['meta']['templates_used']
+
+print '#2: test get_data_set... '
+d = get_data_set(event_json)

### 2016-11-03 h3lib.learn.api/test/testQuickTemplate.py

@@ -1,0 +1,14 @@
+from SmartEngine.MyClassifier import *
+from SmartEngine.QuickTemplate import *
+
+clf = QuickTemplate()
+x = np.random.rand(50,2)
+y = np.random.choice([1,-1], 50)
+clf.train(x,y)
+clf.update(x,y)
+clf.save('tmp.checkpoint')
+xtt = np.random.rand(50,2)
+ytt = np.random.choice([1,-1], 50)
+clf2 = dill.load(open('tmp.checkpoint'))
+y_pred = clf2.predict(xtt)
+print 'mean error ', (ytt-y_pred).mean()

### 2016-11-03 h3lib.learn.api/utils/DatasetViewer.py

@@ -1,0 +1,160 @@
+"""
+This utility helper file is used for visualizing a dataset from .csv file.
+The main usage of this file is for easy check how the training dataset looks like,
+and to give developers a quick overview of the data they are dealing with.
+
+Author: Huang Xiao
+Email: xh0217@gmail.com
+Copyright@2016, Stanford
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+from sklearn.decomposition import PCA, KernelPCA
+from sklearn.manifold import MDS
+import getopt,sys,os.path
+import plot_utils as pltool
+
+class DatasetViewer(object):
+    '''
+    A class for dataset viewer used to analyse features in data
+    set straightforwardly
+    '''
+    def __init__(self):
+        pass
+
+    def view_features_distribution(self, X):
+        n,d = X.shape
+        indices = []
+        for i in np.arange(d):
+            indices.extend((i+1)*np.ones(n))
+        plt.gca().scatter(np.asarray(indices), X.T.flatten(),
+                          s=5, marker='.', alpha=0.5,facecolor='None',edgecolor='k')
+        plt.gca().plot([1,d],[0,0],'k-')
+        plt.gca().set(xlabel='feature id',
+                      ylabel='feature value',
+                      title='Feature distribution',
+                      xlim=[0,d-1])
+
+    def project2d(self, X, y=None, method='pca', g=0.5):
+        '''
+        Project high-dimensiona data to 2D for visulaization
+        using methods e.g., pca, kernel-pca, mds
+        :param X: N*d dataset
+        :param y: labels/None if not given
+        :param method: string in ['pca','kpca','mds']
+        :return: projected dataset X_project
+        '''
+        if y is not None and y.size != X.shape[0]:
+            exit("Data dims are not matched!")
+        else:
+            n_comp = 2
+            if method == 'pca':
+                projector = PCA(n_components=n_comp)
+                X_proj = projector.fit_transform(X)
+            elif method == 'kpca':
+                projector = KernelPCA(n_components=n_comp,kernel='rbf',gamma=g)
+                X_proj = projector.fit_transform(X)
+            elif method == 'mds':
+                projector = MDS(n_components=n_comp)
+                X_proj = projector.fit_transform(X)
+            else:
+                print 'No projector found!'
+                X_proj = X
+
+        if y is not None:
+            plt.gca().scatter(X_proj[:,0], X_proj[:,1], c=y, alpha=0.4)
+        else:
[…]

### 2016-11-03 h3lib.learn.api/utils/__init__.py

@@ -1,1 +1,0 @@
-__author__ = 'morgan'

### 2016-11-03 h3lib.learn.api/utils/dataset_helper.py

@@ -1,0 +1,87 @@
+"""
+This utility file contains helper functions for dataset preparation. It is intended for preparing
+datasets used in other places.
+
+Author: Huang Xiao
+Email: xh0217@gmail.com
+Copyright@2016, Stanford
+"""
+
+import json
+
+def get_data_batch(events_json):
+    '''
+    Return a dataset in a single batch from events json file
+    :param events_json: filename of events JSON
+    :return: dict contain dataset
+    '''
+
+    fd = open(events_json, 'r')
+    content = fd.read()
+    data = json.loads(content)
+    res = dict()
+    cnt_in = 0
+    cnt_out = 0
+    template_list = set()
+    for row in data:
+        ACTION = row[0]
+        TIMESTAMP = row[1]
+        CAMPAIGN_ID = row[2]
+        EMAIL_IDs = row[3]
+        CONTENT = row[4]
+
+        # form the dictionary
+        if ACTION == 'IN':
+            # check if the keys exist
+            if not res.has_key(CAMPAIGN_ID):
+                res[CAMPAIGN_ID] = dict()
+            if not res[CAMPAIGN_ID].has_key(EMAIL_IDs):
+                res[CAMPAIGN_ID][EMAIL_IDs] = dict()
+            # update values
+            res[CAMPAIGN_ID][EMAIL_IDs]['timestamp'] = TIMESTAMP
+            res[CAMPAIGN_ID][EMAIL_IDs]['content'] = CONTENT
+            cnt_in += 1
+        if ACTION == 'TEMPLATE':
+            for eid in EMAIL_IDs:
+                # check if the keys exist
+                if not res.has_key(CAMPAIGN_ID):
+                    res[CAMPAIGN_ID] = dict()
+                if not res[CAMPAIGN_ID].has_key(eid):
+                    res[CAMPAIGN_ID][eid] = dict()
+                res[CAMPAIGN_ID][eid]['template'] = CONTENT
+                cnt_out += 1
+                if CONTENT:
+                    template_list.add(CONTENT)
+    meta = {'received': cnt_in,
+            'sent': cnt_out,
+            'templates_used': list(template_list)}
+    res['meta'] = meta
+    print '[INFO] Total received {:d} mails and sent {:d} mails with {:d} different templates.'.format(cnt_in, cnt_out, len(template_list))
+    return res
+
+def get_data_set(events_json):
+    '''
+    Get a trainable dataset from the events JSON file, note that only emails with template ID are returned
[…]

### 2016-11-03 h3lib.learn.api/utils/plot_utils.py

@@ -1,4 +1,10 @@
-__author__ = 'morgan'
+"""
+This utility file contains helper functions for facilitating plotting
+
+Author: Huang Xiao
+Email: xh0217@gmail.com
+Copyright@2016, Stanford
+"""
 
 import numpy as np
 

### 2016-11-03 h3lib.learn.api/main.py
test->main

@@ -1,0 +1,3 @@
+'''
+test code
+'''

### 2016-11-03 h3lib.learn.api/test.py

@@ -1,79 +1,0 @@
-import pickle
-import numpy as np
-import matplotlib.pyplot as plt
-from sklearn.decomposition import PCA, KernelPCA
-from sklearn.naive_bayes import GaussianNB
-from sklearn.ensemble import RandomForestClassifier as RFClassifier
-from sklearn.linear_model import SGDClassifier
-from sklearn.manifold import MDS
-from sklearn.svm import SVC
-from utils import plot_utils
-from sklearn import cross_validation as cv
-from sklearn.grid_search import GridSearchCV
-from sklearn.datasets import load_digits
-import random
-
-# preconfigure dataset
-# ----- read MyriadHub data from JSON file
-#mydata = pickle.load(open('../feed_dataset.p', 'rb'))
-#Xtr = mydata['vectors'].todense()
-#ytr = np.array(mydata['labels'])
-## multiple labels
-#original_labels = ytr.copy()
-## binary labels
-#ytr[ytr!=0] = 1
-#ytr[ytr==0] = -1
-#print "here1"
-
- #test digits dataset
-digits = load_digits()
-Xtr = digits.data
-original_labels = digits.target
-
-# initialize classifiers
-#clf_svm_part = SVC(kernel='rbf', C=20, gamma=20, class_weight='auto') #n_iter = 1
-#clf_svm = SVC(kernel='rbf', C=20, gamma=20, class_weight='auto')
-#clf_gaussnb = GaussianNB()
-#clf_randforest = RFClassifier(n_estimators=10)
-#clf_logreg = SGDClassifier(loss="log", warm_start=True, alpha=0.0001)
-print "here2"
-
-# model selection for all classifiers 
-#model_selector_svm_part =  ?
-#model_selector_svm = GridSearchCV(estimator=clf_svm, param_grid=dict(C=np.logspace(0.1,10,10),
-#                                                      gamma=np.logspace(0.1,10,10)),
-#                      verbose=1)
-#model_selector_gaussnb = GridSearchCV(estimator=clf_gaussnb, param_grid=dict(),
-#                      verbose=1)
-#model_selector_randforest = GridSearchCV(estimator=clf_randforest, param_grid=dict(n_estimators=range(2,21)),
-#                      verbose=1)
-#model_selector_logreg = GridSearchCV(estimator=clf_logreg, param_grid=dict(alpha=np.logspace(0.0001,50,10)),
-#                      verbose=1)
-print "here3"
-
[…]

### 2016-11-03 h3lib.learn.api/engine/QuickTemplate.py
- reorganize 2

@@ -10,12 +10,12 @@ Email: xh0217@gmail.com
 Copyright@2016, Stanford
 """
 
-from Preprocessor import *
+from engine.Preprocessor import *
 import numpy as np
 from sklearn.grid_search import GridSearchCV
 from sklearn.linear_model import SGDClassifier
 from datetime import datetime
-from MyClassifier import MyClassifier
+from engine.MyClassifier import MyClassifier
 
 
 class QuickTemplate(MyClassifier):

### 2016-11-03 h3lib.learn.api/main.py

@@ -1,3 +1,3 @@
 '''
-test code
+main entry
 '''

### 2016-11-03 h3lib.learn.api/test/testDataBatchHelper.py

@@ -1,4 +1,4 @@
-from SmartEngine.utils.dataset_helper import *
+from utils.dataset_helper import *
 
 event_json = '../../fixed2-mlTestCampaignCuris1.json'
 

### 2016-11-03 h3lib.learn.api/test/testQuickTemplate.py

@@ -1,5 +1,5 @@
-from SmartEngine.MyClassifier import *
-from SmartEngine.QuickTemplate import *
+from engine.MyClassifier import *
+from QuickTemplate import *
 
 clf = QuickTemplate()
 x = np.random.rand(50,2)

### 2016-11-03 h3lib.learn.api/test/testQuickTemplate.py
delete pic

@@ -1,5 +1,5 @@
 from engine.MyClassifier import *
-from QuickTemplate import *
+from engine.QuickTemplate import *
 
 clf = QuickTemplate()
 x = np.random.rand(50,2)

### 2016-11-03 h3lib.learn.api/engine/Preprocessor.py
- rectify code

@@ -30,7 +30,7 @@ class Preprocessor(object):
         self._FEATURE_NAMES = feature_names
         self._FEATURE_SIZE = 0
         for elem in pipeline:
-            worker_class = getattr(importlib.import_module("SmartEngine.PipelineWorkers"), elem['worker'])
+            worker_class = getattr(importlib.import_module("PipelineWorkers"), elem['worker'])
             if elem.has_key('params'):
                 worker = worker_class(elem['params'])
             else:

### 2016-11-03 h3lib.learn.api/engine/QuickTemplate.py

@@ -10,12 +10,12 @@ Email: xh0217@gmail.com
 Copyright@2016, Stanford
 """
 
-from engine.Preprocessor import *
+from Preprocessor import *
 import numpy as np
 from sklearn.grid_search import GridSearchCV
 from sklearn.linear_model import SGDClassifier
 from datetime import datetime
-from engine.MyClassifier import MyClassifier
+from MyClassifier import MyClassifier
 
 
 class QuickTemplate(MyClassifier):
@@ -46,7 +46,8 @@ class QuickTemplate(MyClassifier):
       self.shuffle = shuffle
       if preprocessor is None:
          # the default preprocessor is a Tfidf vectorizer
-         self.preprocessor = Preprocessor(pipeline=[('TfidfVectorizer', {'encoding': 'utf-8'})])
+         workflow_1 = [{'worker': 'TfidfVectorizer', 'params': {'encoding': 'utf-8'}}]
+         self.preprocessor = [Preprocessor(workflow_1, ['n-grams'])]
       else:
          self.preprocessor = preprocessor
       # default classifier is SGD logistic regressor

### 2016-11-04 ml.core/test/testSnippetSecurity.py
add testcode

@@ -1,0 +1,24 @@
+'''
+A Java snippet security detector using TfIdf
+'''
+import csv, datetime
+from ..engine import PipelineWorkers, Preprocessor, QuickTemplate
+
+# process input data
+raw_data_path = '~/repos/h3lib/h3db/snippet_data.csv'
+with open(raw_data_path, 'rb') as csv_file:
+   samples = csv.reader(csv_file, delimiter=',')
+   X, y = list(), list()
+   for id, sample in enumerate(samples):
+      X.append(sample[0])
+      y.append(int(sample[1]))
+      if id % 100 == 0:
+         print '{:d} samples are processed ... '.format(id)
+
+# prepare classifier
+work_flow = [{'worker': 'TfIdfVectorizer', 'params': {'encoding': 'utf-8'}},
+             {'worker': 'FeatureScaler', 'params': {'type': 'minmax'}}]
+pp = Preprocessor.Preprocessor(work_flow)
+SnippetClf = QuickTemplate.QuickTemplate(preprocessor=[pp])
+
+

### 2016-11-04 ml.core/engine/Preprocessor.py
- test java snippet code ready

@@ -30,7 +30,7 @@ class Preprocessor(object):
         self._FEATURE_NAMES = feature_names
         self._FEATURE_SIZE = 0
         for elem in pipeline:
-            worker_class = getattr(importlib.import_module("PipelineWorkers"), elem['worker'])
+            worker_class = getattr(importlib.import_module("engine.PipelineWorkers"), elem['worker'])
             if elem.has_key('params'):
                 worker = worker_class(elem['params'])
             else:

### 2016-11-04 ml.core/main.py

@@ -1,3 +1,5 @@
 '''
 main entry
 '''
+
+import test.testSnippetSecurity

### 2016-11-04 ml.core/test/testSnippetSecurity.py

@@ -1,24 +1,73 @@
 '''
 A Java snippet security detector using TfIdf
 '''
-import csv, datetime
-from ..engine import PipelineWorkers, Preprocessor, QuickTemplate
+import csv, sys, datetime as dt
+import numpy as np
+from peewee import *
 
-# process input data
-raw_data_path = '~/repos/h3lib/h3db/snippet_data.csv'
+sys.path.append('../')
+from engine.QuickTemplate import QuickTemplate
+from engine.Preprocessor import Preprocessor
+from sklearn.cross_validation import StratifiedKFold
+from sklearn.metrics import accuracy_score, f1_score
+
+
+class JavaSnippets(Model):
+   '''
+    Data Model for JavaSnippet Instance
+    '''
+
+   class Meta:
+      database = MySQLDatabase('java_snippets_sec_db', host="localhost", user="root", passwd="damnshit")
+
+   snippet_id = IntegerField()
+   snippet = TextField(null=True)
+   true_sec_level = IntegerField(null=True, default=0)
+   predict_sec_level = IntegerField(null=True, default=0)
+
+db = JavaSnippets._meta.database
+db.connect()
+db.create_tables([JavaSnippets], safe=True)
+
+raw_data_path = '/Users/hxiao/repos/h3lib/h3db/snippet_data.csv'
 with open(raw_data_path, 'rb') as csv_file:
    samples = csv.reader(csv_file, delimiter=',')
    X, y = list(), list()
    for id, sample in enumerate(samples):
       X.append(sample[0])
       y.append(int(sample[1]))
-      if id % 100 == 0:
+      if id > 0 and id % 100 == 0:
          print '{:d} samples are processed ... '.format(id)
+      if JavaSnippets.select().where(JavaSnippets.snippet_id == id).count() == 0:
+         # insert new row
+         snippet = JavaSnippets()
+         snippet.snippet_id = id
+         snippet.snippet = sample[0]
+         snippet.true_sec_level = sample[1]
+         snippet.save()
 
 # prepare classifier
-work_flow = [{'worker': 'TfIdfVectorizer', 'params': {'encoding': 'utf-8'}},
+work_flow = [{'worker': 'TfidfVectorizer', 'params': {'encoding': 'utf-8'}},
[…]

### 2016-11-04 ml.core/test/testSnippetSecurity.py
- add command line parser

@@ -1,7 +1,7 @@
 '''
 A Java snippet security detector using TfIdf
 '''
-import csv, sys, datetime as dt
+import csv, sys, datetime as dt, argparse
 import numpy as np
 from peewee import *
 
@@ -29,8 +29,13 @@ db = JavaSnippets._meta.database
 db.connect()
 db.create_tables([JavaSnippets], safe=True)
 
-raw_data_path = '/Users/hxiao/repos/h3lib/h3db/snippet_data.csv'
+argparser = argparse.ArgumentParser()
+argparser.add_argument("--filename", help="input snippet csv file path...")
+args = argparser.parse_args()
+raw_data_path = args.filename
+
 with open(raw_data_path, 'rb') as csv_file:
+   print 'Cross validation on file: {:s}'.format(raw_data_path)
    samples = csv.reader(csv_file, delimiter=',')
    X, y = list(), list()
    for id, sample in enumerate(samples):

### 2016-11-05 mlcore/test/testSnippetSecurity.py
rename folder

@@ -3,37 +3,26 @@ A Java snippet security detector using TfIdf
 '''
 import csv, sys, datetime as dt, argparse
 import numpy as np
-from peewee import *
 
-sys.path.append('../')
-from engine.QuickTemplate import QuickTemplate
-from engine.Preprocessor import Preprocessor
+sys.path.append('/Users/h3xiao/repos/h3lib/')
+from h3db.model import JavaSnippets
+from ml.core.engine.QuickTemplate import QuickTemplate
+from ml.core.engine.Preprocessor import Preprocessor
 from sklearn.cross_validation import StratifiedKFold
 from sklearn.metrics import accuracy_score, f1_score
 
-
-class JavaSnippets(Model):
-   '''
-    Data Model for JavaSnippet Instance
-    '''
-
-   class Meta:
-      database = MySQLDatabase('java_snippets_sec_db', host="localhost", user="root", passwd="damnshit")
-
-   snippet_id = IntegerField()
-   snippet = TextField(null=True)
-   true_sec_level = IntegerField(null=True, default=0)
-   predict_sec_level = IntegerField(null=True, default=0)
-
+# initialize database
 db = JavaSnippets._meta.database
 db.connect()
 db.create_tables([JavaSnippets], safe=True)
 
+# initialize command parser
 argparser = argparse.ArgumentParser()
 argparser.add_argument("--filename", help="input snippet csv file path...")
 args = argparser.parse_args()
 raw_data_path = args.filename
 
+# parse raw data
 with open(raw_data_path, 'rb') as csv_file:
    print 'Cross validation on file: {:s}'.format(raw_data_path)
    samples = csv.reader(csv_file, delimiter=',')
@@ -58,6 +47,8 @@ pp = Preprocessor(work_flow)
 SnippetClf = QuickTemplate(preprocessor=[pp])
 Xtr = SnippetClf.prep_data(data_blocks=[X])
 ytr = np.array(y)
+
+# do cross validation
 cvfolds = StratifiedKFold(ytr, n_folds=5)
 fold_id = 0
 for tr_idx, tt_idx in cvfolds:

### 2016-11-05 h3db/model/JavaSnippets.py
- add h3db files - ignore updated

@@ -1,0 +1,15 @@
+from peewee import Model, MySQLDatabase, IntegerField, TextField
+
+
+class JavaSnippets(Model):
+   '''
+    Data Model for JavaSnippet Instance
+    '''
+
+   class Meta:
+      database = MySQLDatabase('java_snippets_sec_db', host="localhost", user="root", passwd="damnshit")
+
+   snippet_id = IntegerField()
+   snippet = TextField(null=True)
+   true_sec_level = IntegerField(null=True, default=0)
+   predict_sec_level = IntegerField(null=True, default=0)

### 2016-11-05 mlcore/engine/MyClassifier.py
- rectify codes

@@ -60,7 +60,7 @@ class MyClassifier(object):
         # save checkpoint for the predictive model
         dill.dump(self, open(path, 'w'))
         if self.verbose:
-            print '\t[INFO][{:s}] classifier checkpoint is saved at {:s} ...'.format(datetime.now().strftime('%Y-%m-%d %H:%M:%S'),
+            print '[INFO][{:s}] classifier checkpoint is saved at {:s} ...'.format(datetime.now().strftime('%Y-%m-%d %H:%M:%S'),
                                                                     path)
 
     def add_preprocessor(self, pc):

### 2016-11-05 mlcore/engine/Preprocessor.py

@@ -30,7 +30,7 @@ class Preprocessor(object):
         self._FEATURE_NAMES = feature_names
         self._FEATURE_SIZE = 0
         for elem in pipeline:
-            worker_class = getattr(importlib.import_module("engine.PipelineWorkers"), elem['worker'])
+            worker_class = getattr(importlib.import_module("mlcore.engine.PipelineWorkers"), elem['worker'])
             if elem.has_key('params'):
                 worker = worker_class(elem['params'])
             else:

### 2016-11-05 mlcore/engine/QuickTemplate.py

@@ -32,7 +32,7 @@ class QuickTemplate(MyClassifier):
                 shuffle=True,
                 class_weight=None,
                 max_epoch=10,
-                verbose=True):
+                verbose=False):
       """
       Constructor
       :return:
@@ -56,9 +56,6 @@ class QuickTemplate(MyClassifier):
                                alpha=self.alpha,
                                shuffle=self.shuffle,
                                class_weight=class_weight)
-      # if verbose:
-      #     print '[INFO][{:s}] {:s} is initialized.'.format(datetime.now().strftime('%Y-%m-%d %H:%M:%S'),
-      #                                                  self.name)
 
    def train(self, trainset, labels=None):
       """

### 2016-11-05 mlcore/test/testQuickTemplate.py

@@ -1,5 +1,5 @@
-from engine.MyClassifier import *
-from engine.QuickTemplate import *
+from mlcore.engine.MyClassifier import *
+from mlcore.engine.QuickTemplate import *
 
 clf = QuickTemplate()
 x = np.random.rand(50,2)

### 2016-11-05 mlcore/test/testSnippetSecurity.py

@@ -1,15 +1,13 @@
 '''
 A Java snippet security detector using TfIdf
 '''
-import csv, sys, datetime as dt, argparse
+import csv, datetime as dt, argparse
 import numpy as np
-
-sys.path.append('/Users/h3xiao/repos/h3lib/')
-from h3db.model import JavaSnippets
-from ml.core.engine.QuickTemplate import QuickTemplate
-from ml.core.engine.Preprocessor import Preprocessor
+from h3db.model.JavaSnippets import *
+from mlcore.engine.QuickTemplate import QuickTemplate
+from mlcore.engine.Preprocessor import Preprocessor
 from sklearn.cross_validation import StratifiedKFold
-from sklearn.metrics import accuracy_score, f1_score
+from sklearn.metrics import accuracy_score
 
 # initialize database
 db = JavaSnippets._meta.database
@@ -64,6 +62,7 @@ for tr_idx, tt_idx in cvfolds:
    fold_id += 1
    for elem in zip(tt_idx, y_predict):
       tid, yt = elem[0], elem[1]
-      query = JavaSnippets.update(predict_sec_level=yt).where(JavaSnippets.snippet_id==tid)
+      query = JavaSnippets.update(predict_sec_level=yt).where(JavaSnippets.snippet_id == tid)
       query.execute()
-
+SnippetClf.train(Xtr, ytr)
+SnippetClf.save('../models/JavaSnippetSecurityDetector-' + dt.datetime.today().date().__str__() + '.ckp')

### 2016-11-05 mlcore/test/testDataBatchHelper.py
- remove databatchhelper

@@ -1,11 +1,0 @@
-from utils.dataset_helper import *
-
-event_json = '../../fixed2-mlTestCampaignCuris1.json'
-
-print '#1: test get_data_batch... '
-res = get_data_batch(event_json)
-json.dump(res, open('temp.json', 'w'))
-print 'templates used: ', res['meta']['templates_used']
-
-print '#2: test get_data_set... '
-d = get_data_set(event_json)

### 2017-06-01 mlcore/main.py
- add ansible and vagrant files

@@ -2,4 +2,20 @@
 main entry
 '''
 
-import test.testSnippetSecurity
+import numpy as np
+import autograd, sys
+import matplotlib.pyplot as plt
+
+def polynomial(w, x, d=3):
+
+   if w.size != d:
+      sys.exit('wrong dim. of weights')
+   d = np.arange(d) + 1
+   return w[0]*x**d[0] + w[1]*x**d[1] + w[2]*x**d[2]
+
+grad_func = autograd.grad(polynomial, 1)
+X, y = np.random.rand(10, 1), np.random.rand(10, 1)
+w_init = np.random.rand(3, 1)
+plt.plot(np.arange(10), X, 'r-')
+plt.plot(np.arange(10), [grad_func(np.array([0.5, 1, -0.5]), X[i], d=3) for i in np.arange(10)], 'g-')
+plt.show()

### 2017-06-01 mlcore/models/H3GPC.py

@@ -75,7 +75,6 @@ class H3GPC(object):
 
 if __name__ == '__main__':
     import matplotlib.pyplot as plt
-    import utils.plot_utils as pltool
     X1 = np.random.multivariate_normal([-2.5, 2.5], [[0.5, 0], [0, 1.5]], 50)
     y1 = np.ones(X1.shape[0])
     X2 = np.random.multivariate_normal([2.5, 2.5], [[1.5, 0], [0, 0.5]], 50)
@@ -88,7 +87,6 @@ if __name__ == '__main__':
     Xt, yt = np.r_[X1t, X2t], np.r_[y1t, y2t]
     plt.plot(X[y == 1, 0], X[y == 1, 1], 'ro')
     plt.plot(X[y == -1, 0], X[y == -1, 1], 'bo')
-    pltool.setAxSquare(plt.gca())
     clf = H3GPC(gamma=0.5)
     ft_mean, ft_var = clf.fit(X, y, Xt)
     print ft_mean, ft_var

### 2017-06-01 mlcore/models/H3GPR.py

@@ -55,7 +55,6 @@ class H3GPR(object):
 
 if __name__ == '__main__':
     import matplotlib.pyplot as plt
-    import utils.plot_utils as pltool
 
     def obj_f(x):
         # 1d objective function
@@ -68,7 +67,7 @@ if __name__ == '__main__':
     ytr = y[given_idx]
     fig = plt.figure(figsize=(16,8))
     for id, g in enumerate(np.linspace(0.1, 10, 4)):
-        gpr = H3GPR(sigma=0, gamma=g)
+        gpr = H3GPR(sigma=1e-3, gamma=g)
         m, S, LL = gpr.fit(Xtr, ytr, X)
         plt.subplot(2, 2, id + 1)
         # randomly sample functions from predictive distribution

### 2017-06-01 mlcore/models/H3iSVC.py

@@ -408,7 +408,7 @@ if __name__ == '__main__':
     # data = savemat("syndata.mat", mdict={'Xtr': Xtr, 'ytr': ytr})
     # data = loadmat('../datasets/syndata.mat')
     # Xtr, ytr = data['X'], data['Y']
-    clf1 = H3iSVC(C=0.1, gamma=2, kernel='rbf', display=True, labeling=True)
+    clf1 = H3iSVC(C=0.2, gamma=2, kernel='rbf', display=True, labeling=True)
     cProfile.run("clf1.fit(Xtr)")
     # from H3iSVC_QP import H3iSVC_QP as svcqp
     # clf2 = svcqp(C=0.05, gamma=1.5, kernel='rbf')

### 2017-09-03 ml_notes/draft.tex
- add ansible and vagrant files
repo clean

@@
 \author{
-	Huang Xiao\thanks{Visiting homepage: feuerchop.github.io} \\
+	Huang Xiao\thanks{Website: www.huangxiao.de} \\
 	Department of Computer Science\\
@@
 A typical feature mapping is polynomial feature mapping. Suppose we have a 2-dimensional input data sample $ \left( x_1, x_2 \right) $, we define a feature mapping as follows,
-\[ \left( x_1, x_2 \right) \rightarrow \left( x_1, x_2, x_1^2+x_2^2 \right)\], where a 2-d plane is transformed as a paraboloid in 3-d space.
+\[ \left( x_1, x_2 \right) \rightarrow \left( x_1, x_2, x_1^2+x_2^2 \right), \] where a 2-d plane is transformed as a paraboloid in 3-d space.
 Substituting back into previous linear function, it becomes a polynomial line fitting problem, but it is still linear in $ \vct w $.
@@
 
+\section{Anomaly Detection: A Survey}
+In this section, I review literatures of importance in regard of anomaly detection in recent years, a more thorough survey of this research domain can be found also in \cite{Hodge2004, Chandola2009}.
+
+\section{Supervised Sequence Labeling}
+The problem of supervised sequence labeling \cite{Graves2013} is to assign a sequence of labels given an input sequence.
+Suppose we have input sequence of length $ m $: $ \vct x_i = \left\lbrace x_i^{0}, x_i^{1}, \ldots, x_i^{m}\right\rbrace $, we aim to learn a function which assigns a sequence of labels $ \vct t_i $ of length $ s $ on $ \vct x_i $.
+That is,
+\begin{align*}
+& f(x_i)  = \vct t_i, \\
+\text{where} \quad & \vct t_i = \left\lbrace t_i^{0}, t_i^{1}, \ldots, t_i^{s}\right\rbrace
+\end{align*}                 
+For supervised sequence labeling, there's training labels available and accordingly there're
+typically three types of learning tasks in sequence labeling.
+
+\begin{description}
+	\item[Sequence Classification] 
+	It seeks a discriminative classification function to assign 
+	singular label to a whole input sequence. This is a \textit{m-vs-1} relationship.
+	For instances, a sentence type classifier automatically assigns a sentence to a type
+	label. \textit{Who is president of USA?} is a \textit{question} sentence.
+
+	Error function for sequence classification can be as easy as normal binary or multiclass
+	classification problem, e.g., using softmax cross entropy to measure the loss.
+
+	\item[Segment Classification] 
+	Different from sequence classification, segment classifcation generates a shorter sequence 
+	of labels that are assigned to segments of sequence. This is a \textit{m-vs-s} relationship.
+	Namely we have $ | \vct t_i | < | \vct x_i |$. This is analog to image segmenation which 
+	learns to segment image to different objects.
+
+	Error function for segment classification can be set as percentage of misclassified segments.
+	Denote the a test sequence dataset $S' = \left\lbrace (\vct x_i, \vct z_i)_{i=1}^N \right\rbrace$,
+	and a segment classification function $h(\cdot)$, the segment error can be defined as, 
+	\[
+		E^{seg}(h, S') = \frac{1}{Z}\sum_{(x,z)\in S'} \text{HD}(h(x), z),
+	\]
+	where \textbf{HD} is the hamming distance between two equal length sequences.
+
+	\item[Temporal Classification] 
+	Temporal classification is a \textit{N-vs-N} relationship. Each step of input sequence 
+	generates a output label, it turns out the output length shall be equal to input sequence
+	length.
+
+	A simple error function can be defined as edit distance of two sequences, namely the minimal
+	number of \textit{insertions, substitutions and deletions}. 
+	\[
+		E^{Temp}(h, S') = \frac{1}{Z}\sum_{(x,z)\in S'} \text{ED}(h(x), z),
+	\]
+	where \textbf{ED} is edit distance.
+
+\end{description}
+
 \bibliography{myrefs}
+\bibliographystyle{plain}
 \bibliographystyle{icml2016}

### 2017-09-03 scripts/rabbitmq_receiver.py

@@ -1,0 +1,36 @@
+# msg consumer
+import pika, time, sys
+
+def callback(ch, method, properties, body):
+   print ("[x] Received %r" % body)
+   time.sleep(body.count(b'.'))
+   # print '[x] done!'
+   ch.basic_ack(delivery_tag=method.delivery_tag)
+
+# setup connection
+connection = pika.BlockingConnection(pika.ConnectionParameters('localhost'))
+# get a channel
+channel = connection.channel()
+# declare an exchange
+channel.exchange_declare(exchange="logs",
+                         exchange_type="direct")
+# declare a queue and bind exchange
+q = channel.queue_declare(exclusive=True)
+p = channel.queue_declare(exclusive=True)
+
+# setup routing key
+key = sys.argv[1]
+channel.queue_bind(exchange="logs",
+                   routing_key=key,
+                   queue=q.method.queue)
+channel.queue_bind(exchange="logs",
+                   routing_key='default',
+                   queue=p.method.queue)
+# consuming
+# channel.basic_qos(prefetch_count=1)
+channel.basic_consume(callback,
+                      queue=q.method.queue)
+channel.basic_consume(callback,
+                      queue=p.method.queue)
+print '[*] waiting for messages. To exit press CTRL+C'
+channel.start_consuming()

### 2017-09-03 scripts/rabbitmq_sender.py

@@ -1,0 +1,32 @@
+import sys, pika, time
+import numpy as np
+
+# setup connection to rabbitmq 'localhost'
+connection = pika.BlockingConnection(pika.ConnectionParameters('localhost'))
+# get a channel
+channel = connection.channel()
+# declare an exchange
+channel.exchange_declare(exchange="logs",
+                         exchange_type='direct')
+# create a msg
+cnt = int(sys.argv[1])
+message = ' '.join(sys.argv[2:]) or "Hello World!"
+# declare a queue
+# channel.queue_declare(queue='task_q')
+for id in range(0, cnt):
+   msg = ' '.join([message, str(id)])
+   time.sleep(2*np.random.rand())
+   # publish the msg
+   if id%2 == 0:
+      channel.basic_publish(exchange='logs',
+                            routing_key='even',
+                            body='even number: ' + msg,
+                            properties=pika.BasicProperties(delivery_mode=2))
+   else:
+      channel.basic_publish(exchange='logs',
+                            routing_key='odd',
+                            body='odd number: ' + msg,
+                            properties=pika.BasicProperties(delivery_mode=2))
+   print "[x] Sent %r" % msg
+# close the channel
+channel.close()

### 2017-09-03 scripts/tfexamples/tf_convnet.py

@@ -10,93 +10,94 @@ Project: https://github.com/aymericdamien/TensorFlow-Examples/
 from __future__ import print_function
 
 import tensorflow as tf
+import matplotlib.pyplot as plt
+import numpy as np
 
 # Import MNIST data
 from tensorflow.examples.tutorials.mnist import input_data
+
 mnist = input_data.read_data_sets("/tmp/data/", one_hot=True)
 
 # Parameters
 learning_rate = 0.001
-training_iters = 200000
+training_iters = 20000
 batch_size = 128
 display_step = 10
 
 # Network Parameters
-n_input = 784 # MNIST data input (img shape: 28*28)
-n_classes = 10 # MNIST total classes (0-9 digits)
-dropout = 0.75 # Dropout, probability to keep units
+n_input = 784  # MNIST data input (img shape: 28*28)
+n_classes = 10  # MNIST total classes (0-9 digits)
+dropout = 0.75  # Dropout, probability to keep units
 
 # tf Graph input
 x = tf.placeholder(tf.float32, [None, n_input])
 y = tf.placeholder(tf.float32, [None, n_classes])
-keep_prob = tf.placeholder(tf.float32) #dropout (keep probability)
+keep_prob = tf.placeholder(tf.float32)  # dropout (keep probability)
 
 
 # Create some wrappers for simplicity
 def conv2d(x, W, b, strides=1):
-    # Conv2D wrapper, with bias and relu activation
-    x = tf.nn.conv2d(x, W, strides=[1, strides, strides, 1], padding='SAME')
-    x = tf.nn.bias_add(x, b)
-    return tf.nn.relu(x)
+   # Conv2D wrapper, with bias and relu activation
+   x = tf.nn.conv2d(x, W, strides=[1, strides, strides, 1], padding='SAME')
+   x = tf.nn.bias_add(x, b)
+   return tf.nn.relu(x)
 
 
 def maxpool2d(x, k=2):
-    # MaxPool2D wrapper
-    return tf.nn.max_pool(x, ksize=[1, k, k, 1], strides=[1, k, k, 1],
-                          padding='SAME')
+   # MaxPool2D wrapper
+   return tf.nn.max_pool(x, ksize=[1, k, k, 1], strides=[1, k, k, 1],
+                         padding='SAME')
 
 
 # Create model
 def conv_net(x, weights, biases, dropout):
-    # Reshape input picture
[…]

### 2017-09-03 mlcore/setup.py
clean and further maintain

@@ -1,3 +1,15 @@
 #!/usr/bin/env python
 
+from distutils.core import setup
+
+setup(
+    name='h3mlcore',
+    version='0.1dev',
+    url='https://github.com/feuerchop/h3lib/tree/master/mlcore'
+    packages=['mlcore',],
+    license='Creative Commons Attribution-Noncommercial-Share Alike license',
+    long_description=open('README.md').read(),
+)
+
+
 

### 2017-09-03 mlcore/views/apps/BayeNet.py
maintain

@@ -1,35 +1,0 @@
-import cherrypy
-import jinja2 as jj2
-from mlcore.utils.dataset_helper import read_csv
-from mlcore.models.H3BayesNet import H3BayesNet
-
-
-class BayesNet(object):
-   def __init__(self):
-      self.env = jj2.Environment(loader=jj2.FileSystemLoader('./templates/BayesNet/'))
-      self.UPLOADED_DIR = cherrypy.config['uploads_path']
-      self.CSV_FILE = ''
-
-   @cherrypy.expose
-   def index(self):
-      return self.env.get_template('index.html').render()
-
-   @cherrypy.expose
-   def draw(self, upload_input):
-      # handle the uploaded file
-      template = self.env.get_template('index.html')
-      # upload file first
-      file_uploaded = self.UPLOADED_DIR + upload_input.filename
-      with open(file_uploaded, 'w+') as f:
-         f.writelines(upload_input.file.readlines())
-         f.flush()
-      cherrypy.log("[INFO] New dataset .csv file: {} successfully uploaded!".format(upload_input.filename))
-      f.close()
-      self.CSV_FILE = file_uploaded
-      Xtr, nodes = read_csv(self.CSV_FILE)
-      clf = H3BayesNet(alpha=0.1, vnames=nodes, method='ledoit_wolf', penalty=1.0)
-      clf.fit(Xtr)
-      ci_coef = clf.ci_coef_
-      adjmat = clf.conditional_independences_
-      # TODO: ajax reload
-      return template.render(ci_coef=ci_coef, adjmat=adjmat)

### 2017-09-03 mlcore/views/apps/DialogType.py

@@ -1,396 +1,0 @@
-import os, re, nltk, pickle, dill, json, cherrypy
-import numpy as np, jinja2 as jj2
-from scipy.spatial.distance import pdist, squareform
-from sklearn.feature_extraction.text import CountVectorizer, TfidfVectorizer
-from sklearn.manifold import TSNE
-from sklearn.linear_model import SGDClassifier
-from nltk.tokenize import TreebankWordTokenizer, RegexpTokenizer
-from bokeh.plotting import figure
-from bokeh.embed import components
-from bokeh.models import ColumnDataSource, LabelSet
-
-env = jj2.Environment(loader=jj2.FileSystemLoader('./templates/DialogType'))
-
-class Mails(object):
-   def __init__(self):
-      # NEED TO RESET PATH IF WEB RUNS ALONE
-      self.TRAIN_MODEL_PATH = cherrypy.config['checkpoints_path']
-      self.DATAPATH = cherrypy.config['data_path']
-      # Where we save user uploaded JSON file
-      self.UPLOADED_DIR = cherrypy.config['uploads_path']
-      # MUST COMPLY A CERTAIN JSON FORMAT, DEFAULT WITH A SIMPLE CAMPAGIN
-      # FILE
-      self.CAMPAIGN_FILE = ''.join([self.UPLOADED_DIR, 'feed.json'])
-      # Pretrained Glove word embedding JSON dataset used as Lookup table
-      # See more: http://nlp.stanford.edu/projects/glove/
-      self.GLOVE_SET = ''.join([self.DATAPATH, 'glove.twitter.27B.25d.json'])
-      self.CAMPAIGN_VECTORS = ''.join([self.DATAPATH, self.CAMPAIGN_FILE.split('/')[-1].split('.')[0], '.vectors.json'])
-      self.CAMPAIGN_KNN = ''.join([self.DATAPATH, self.CAMPAIGN_FILE.split('/')[-1].split('.')[0], '.knn.json'])
-
-   def softmax(self, x):
-      """Compute softmax values for each sets of scores in x."""
-      sf = np.exp(x)
-      sf = sf / np.sum(sf, axis=0)
-      return sf
-
-   def retrainModel(self):
-
-      # build classifier for act type on NPS chat dataset
-      # see: http://faculty.nps.edu/cmartell/NPSChat.htm
[…]

### 2017-09-03 mlcore/views/apps/Home.py

@@ -1,11 +1,0 @@
-import cherrypy
-import jinja2 as jj2
-
-class Home(object):
-   def __init__(self):
-      self.env = jj2.Environment(loader=jj2.FileSystemLoader('./templates/Home'))
-
-   @cherrypy.expose
-   def index(self):
-      app_list = cherrypy.request.app.config['APPS']['app_list']
-      return self.env.get_template('index.html').render(apps=app_list)

### 2017-09-03 mlcore/views/public/js/bayesnet_draw.js

@@ -1,118 +1,0 @@
-$(document).ready(function() {
-   var ci_coef = "{{ ci_coef }}"
-   var adjmat = "{{ adjmat }}"
-   console.log(ci_coef);
-   console.log(adjmat);
-   var g = cytoscape({
-      container: $('#graph_canvas'),
-
-      elements: [ // list of graph elements to start with
-         { // node a
-            data: {
-               id: 'a'
-            }
-         },
-         { // node b
-            data: {
-               id: 'b'
-            }
-         },
-         { // node b
-            data: {
-               id: 'c'
-            }
-         },
-         { // node b
-            data: {
-               id: 'd'
-            }
-         },
-         { // edge ab
-            data: {
-               id: 'ab',
-               source: 'a',
-               target: 'b'
-            }
-         },
-         { // edge ab
-            data: {
-               id: 'ac',
-               source: 'a',
-               target: 'c'
-            }
-         },
-         { // edge ab
-            data: {
-               id: 'bc',
-               source: 'b',
-               target: 'c'
-            }
-         },
-         {
-            data: {
-               id: 'cd',
-               source: 'c',
-               target: 'd'
-            }
-         }
-      ],
-
-      style: [ // the stylesheet for the graph
-         {
-            selector: 'node',
-            style: {
-               'background-color': '#177',
-               'label': 'data(id)',
-               'width': 10,
-               'height': 10
-            }
-         },
-
-         {
-            selector: 'edge',
-            style: {
-               'width': 2,
-               'line-color': '#ccc',
-               'target-arrow-color': '#ccc',
-               'target-arrow-shape': 'triangle'
-            }
-         }
-      ],
-
-      layout: {
-         name: 'grid',
-         rows: 2
-      },
-
-      // initial viewport state:
-     zoom: 1,
-     pan: { x: 0, y: 0 },
-
-     // interaction options:
-     minZoom: 1e-50,
-     maxZoom: 1e50,
-     zoomingEnabled: true,
-     userZoomingEnabled: true,
-     panningEnabled: true,
-     userPanningEnabled: true,
-     boxSelectionEnabled: false,
-     selectionType: 'single',
-     touchTapThreshold: 8,
-     desktopTapThreshold: 4,
-     autolock: false,
-     autoungrabify: false,
-     autounselectify: false,
-
-     // rendering options:
-     headless: false,
-     styleEnabled: true,
[…]

### 2017-09-03 mlcore/views/public/js/myscript.js

@@ -1,85 +1,0 @@
-function updateTags(thres) {
-    // use this function to hide tags less than certain probability
-    $(".badge").each(function() {
-        if (parseFloat($(this).html().trim(), 10) <= thres) {
-            $(this).parent().hide();
-        } else {
-            $(this).parent().show();
-        }
-    });
-}
-
-$.expr[':'].containsIgnoreCase = function(n, i, m) {
-    return jQuery(n).text().toUpperCase().indexOf(m[3].toUpperCase()) >= 0;
-};
-
-
-$(document).ready(function() {
-   // var elem = document.querySelector('.js-range');
-   // var init = new Powerange(elem, {min: 0, max: 1, step: 0.02, decimal: true, hideRange: true});
-   // we plot
-   $('div#we_modal').hide();
-   $('#we_modal_btn').on("click", function(e) {
-     $("div#we_modal").modal('toggle');
-   });
-
-   // search similar words and highlight them
-   $("#search_similar_btn").click(function(e) {
-     $.post("/getSimilarWords", {
-             "word": $("#watch_word_input").val()
-         })
-         .done(function(s) {
-             $("span.word_tag").removeClass("label label-info");
-             if ($.isEmptyObject(s)) {
-                $("#alert_msg").html("<b>Not found, not in vocabulary.</b>");
-             } else {
-                $("#alert_msg").html("<b>Similar words found: </b>");
-                for (var w in s) {
-                  //   $("span.word_tag:containsIgnoreCase('" + w + "')").toggleClass("highlighted");
-                    $("span.word_tag").filter(function() {
-                       return $(this).text().trim().toLowerCase() === s[w];
-                    }).addClass("label label-info");
-                    $("#alert_msg").append("<span class='label label-info' style='margin-left: 5px;'>" + s[w] + "</span>");
-                }
-             }
-             $("div.alert").show(200);
-         });
-     e.preventDefault();
-   });
-
-   // hiden alert info when click close
-   $("div.alert button.close").on("click", function(e) {
-      $("div.alert").hide();
-      $("span.word_tag").removeClass("label label-info");
-   });
-
-});
-// $("div.alert").hide();
-// $("#info_btn").click(function(e) {
-//    $.get("/getWordVec")
-//    .done(function(s) {
-//       $("div.alert").html(s);
-//       $("div.alert").show();
-//    });
-//    e.preventDefault();
-// });
-
-// $(".sentence-panel .panel-body").on({
[…]

### 2017-09-03 mlcore/views/simplepage.py

@@ -1,13 +1,0 @@
-import os, cherrypy
-from apps.DialogType import Mails
-from apps.BayeNet import BayesNet
-from apps.Home import Home
-
-
-if __name__ == '__main__':
-   cherrypy.config.update(config='confs/global.cfg')
-   cherrypy.tree.mount(Home(), '/', config='confs/default.cfg')
-   cherrypy.tree.mount(Mails(), '/mails', config='confs/DialogType.cfg')
-   cherrypy.tree.mount(BayesNet(), '/bayesnet', config='confs/BayesNet.cfg')
-   cherrypy.engine.start()
-   cherrypy.engine.block()

### 2017-09-03 mlcore/setup.py
add setup file

@@ -1,15 +1,59 @@
 #!/usr/bin/env python
 
-from distutils.core import setup
+"""A setuptools based setup module.
+See:
+https://packaging.python.org/en/latest/distributing.html
+https://github.com/pypa/sampleproject
+"""
+
+# Always prefer setuptools over distutils
+from setuptools import setup, find_packages
+# To use a consistent encoding
+from codecs import open
+from os import path
+
+"""A setuptools based setup module.
+See:
+https://packaging.python.org/en/latest/distributing.html
+https://github.com/pypa/sampleproject
+"""
+
+# Always prefer setuptools over distutils
+from setuptools import setup, find_packages
+# To use a consistent encoding
+from codecs import open
+from os import path
+
 
 setup(
     name='h3mlcore',
     version='0.1dev',
-    url='https://github.com/feuerchop/h3lib/tree/master/mlcore'
-    packages=['mlcore',],
-    license='Creative Commons Attribution-Noncommercial-Share Alike license',
+    url='https://github.com/feuerchop/h3lib/tree/master/mlcore',
+    packages=find_packages(exclude=['test']),
+    author='Huang Xiao',
+    author_email='xh0217@gmail.com',
+    license='Creative Commons license',
     long_description=open('README.md').read(),
+    classifiers=[
+        # How mature is this project? Common values are
+        #   3 - Alpha
+        #   4 - Beta
+        #   5 - Production/Stable
+        'Development Status :: 3 - Alpha',
+
+        # Indicate who your project is intended for
+        'Intended Audience :: Developers',
+        'Topic :: Scientific/Engineering :: Artificial Intelligence',
+
+        # Pick your license as you wish (should match "license" above)
+
+        # Specify the Python versions you support here. In particular, ensure
+        # that you indicate whether you support Python 2, Python 3 or both.
+        'Programming Language :: Python :: 2',
+        'Programming Language :: Python :: 2.6',
+        'Programming Language :: Python :: 2.7',
+    ],
+
+    keywords='machine learning data mining',
+
 )
-
-
-

### 2017-09-03 mlcore/mlcore/utils/BayesNetHelper.py
update modules and setup file

@@ -24,12 +24,16 @@ base = os.getcwd()
 
 
 def get_neighbors(dag, node):
-   '''
-   Get neighbours of a node
-   :param dag: adjacent matrix
-   :param node: node index
-   :return: unknown, incoming, outgoing
-   '''
+    """Get neighbours of a node
+
+    Args:
+      dag: adjacent matrix
+      node: node index
+
+    Returns:
+      unknown, incoming, outgoing
+
+    """
 
    unknown = list([])
    incoming = list([])
@@ -52,13 +56,17 @@ def get_neighbors(dag, node):
 
 
 def find_path(pdag, p, q):
-   '''
-   Find a path from node p to q using dijisktra algorithm
-   :param pdag: partial DAG
-   :param p: start node p
-   :param q: end node q
-   :return: flag if we can find a path, 1 yes, 0 no
-   '''
+    """Find a path from node p to q using dijisktra algorithm
+
+    Args:
+      pdag: partial DAG
+      p: start node p
+      q: end node q
+
+    Returns:
+      flag if we can find a path, 1 yes, 0 no
+
+    """
 
    flag = 0
    path = []
@@ -90,13 +98,17 @@ def find_path(pdag, p, q):
 
 
 def get_dependencies(dag, p, q):
-   '''
-   return markov blanket of both nodes
-   :param dag: DAG adjecant matrix
-   :param p: node index
-   :param q: node index
-   :return: list of dependent node indices
-   '''
+    """return markov blanket of both nodes
+
+    Args:
+      dag: DAG adjecant matrix
+      p: node index
+      q: node index
+
+    Returns:
+      list of dependent node indices
+
+    """
 
    p_unknown, p_incoming, p_outgoing = get_neighbors(dag, p)
    q_unknown, q_incoming, q_outgoing = get_neighbors(dag, q)
@@ -109,15 +121,20 @@ def get_dependencies(dag, p, q):
 
 
 def is_marriged_edge(graph, corr, p, q, alpha, verbose=False):
-   '''
-   find out if an edge is a married edge brought by colliders, p and q are the nodes of the edge
-   :param graph: undirected graph
-   :param corr: correlation matrix
-   :param p: node index p
-   :param q: node index q
-   :param alpha: threshold alpha
-   :return: flag and colliders
-   '''
+    """find out if an edge is a married edge brought by colliders, p and q are the nodes of the edge
+
+    Args:
+      graph: undirected graph
+      corr: correlation matrix
+      p: node index p
[…]

### 2017-09-03 mlcore/mlcore/utils/DataViz.py

@@ -1,356 +1,0 @@
-"""
-This utility helper file is used for visualizing a dataset from .csv file.
-The main usage of this file is for easy check how the training dataset looks like,
-and to give developers a quick overview of the data they are dealing with.
-
-Author: Huang Xiao
-Email: xh0217@gmail.com
-Copyright@2016, Stanford
-"""
-
-import numpy as np
-from sklearn.decomposition import PCA, KernelPCA
-from sklearn.manifold import MDS
-import getopt, sys, os.path, importlib
-import plot_utils as pltool
-from bokeh.plotting import figure, output_file, show, save
-from bokeh.models import Range1d, BoxZoomTool, PanTool, WheelZoomTool, ResetTool, HoverTool, ResizeTool, SaveTool, \
-   ColumnDataSource
-
-
-class DataViz(object):
-   '''
-   A class for dataset viewer used to analyse features in data
-   set straightforwardly
-   '''
-
-   def __init__(self, config):
-      '''
-      init a dataviz obj for plotting dataset
-      :param config: configuration for plotting
-      :return: a figure handler of bokeh
-      '''
-
-      if config.has_key('dot_size'):
-         self.dot_size = config['dot_size']
-      else:
-         self.dot_size = 4
-      if config.has_key('font_size'):
-         self.font_size = config['font_size']
-      else:
-         self.font_size = 12
-      if config.has_key('line_width'):
-         self.line_width = config['line_width']
-      else:
-         self.line_width = 2
-      if config.has_key('alpha'):
-         self.alpha = config['alpha']
-      else:
-         self.alpha = 0.3
-      if config.has_key('colormap'):
-         # default 3 colors
-         self.colormap = config['colormap']
-      else:
-         # binary colors
-         self.colormap = 'RdYlBu'
-      if config.has_key('color'):
-         self.color = config['color']
-      else:
-         self.color = 'navy'
-      if config.has_key('width'):
-         self.w = config['width']
-      else:
-         self.w = 480
-      if config.has_key('height'):
-         self.h = config['height']
-      else:
-         self.h = 320
-      if config.has_key('output_file'):
-         self.output_file = config['output_file']
-      else:
-         self.output_file = "myplots.html"
-
-      self.binary_colors = ['#4285F4', '#EA4335']
-      self.default_tools = ["pan", "wheel_zoom", "resize", "reset"]
-
-      output_file(self.output_file, title=str.upper(' '.join(self.output_file.split('/')[-1].split('.')[:-1])))
-
-   def _get_figure_instance(self,
[…]

### 2017-09-03 mlcore/setup.py

@@ -27,7 +27,7 @@ from os import path
 
 setup(
     name='h3mlcore',
-    version='0.1dev',
+    version='0.2dev',
     url='https://github.com/feuerchop/h3lib/tree/master/mlcore',
     packages=find_packages(exclude=['test']),
     author='Huang Xiao',
